---
title: "Estimate posterior concordance"
author: "Matt Ploenzke"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Estimate concordance}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Set up and load packages.
```{r setup, include=FALSE}
  rm(list=ls(all=TRUE))
  knitr::opts_chunk$set(echo = TRUE)
  library(PharmacoMixtuR)
  library(tidyverse)
  library(ggridges)
```

Set options.
```{r}
  opt <- list()
  opt$datasets <- c('CCLE','GDSC') # CCLE GDSC GDSC1000 gCSI FIMM CTRPv2
  opt$biomarkers_file <- '~/Desktop/Concordance/PSets/gene_drug_asociations.xlsx'
  #opt$biomarkers_file <- '~/concordance/PSets/gene_drug_asociations.xlsx'
  opt$min_intersection <- 2 # Minimum number of studies a drug/cell must be assayed in to be included in the intersection comparison
  opt$log_dir <- paste(paste(opt$datasets,collapse='_'),'fit_p60',sep='_')
  opt$sensitivity_measure <- c('auc_recomputed') # raw_auc e_inf hill_slope ec50 auc_recomputed
  opt$use_small_datasets <- FALSE
  # Prior specifications denoting cell sensitivity and proportion of drugs broadly-active:
  opt$prior.sensitive <- .6 # .3 # prior specification denoting cell is sensitive if greater than this value
  opt$prior.broadly.active <- 'median_mad' #median .05 # prior specification denoting drug is broadly-active if probability cell is sensitive is greater than value
  opt$run_on_cluster <- FALSE # this just changes file paths depending on where the code is being run
```

Set up log directory.
```{r}
  dir.create(opt$log_dir,showWarnings = FALSE)
  capture.output(opt, file = file.path(opt$log_dir,'model_Opts.csv'))
```

First download the full datasets.
```{r,eval=FALSE}
  PharmacoGx::availablePSets()
  for (dataset in opt$datasets) {
    PharmacoGx::downloadPSet(dataset)
  }
```

Load data.
```{r}
  for (dataset in opt$datasets) {
    if (opt$run_on_cluster) {
      load(file.path('PSets',paste(dataset,'RData',sep='.')))
    } else {
      load(file.path('../PSets',paste(dataset,'RData',sep='.')))
    }
  }
  if (opt$use_small_datasets) {
    CCLE <- PharmacoGx::CCLEsmall
    GDSC <- PharmacoGx::GDSCsmall
  }
```

Format the sensitivity data for each experiment. Find cells and drugs assayed across experiment. Remove noisy experiments and mislabelled cell lines. Calculate sensitivity measures per cell/drug.
```{r}
  sensitivity.tibble.list <- intersectPSetWrapper(datasets = opt$datasets,
                                                  minimum_intersection = 1,
                                                  intersectOn = NULL,
                                                  sensitivity_measure = opt$sensitivity_measure,
                                                  remove_noisy_curves = FALSE,
                                                  remove_mislabelled_cells = FALSE)
```

Repeat but for the intersection.
```{r}
  intersection.tibble.list <- intersectPSetWrapper(datasets = opt$datasets,
                                                  minimum_intersection = opt$min_intersection,
                                                  intersectOn = NULL,
                                                  sensitivity_measure = opt$sensitivity_measure,
                                                  remove_noisy_curves = FALSE,
                                                  remove_mislabelled_cells = FALSE)
  eval(parse(text=paste('rm(',paste(opt$datasets,collapse=','),')',sep='')))
  intersection.tibble.list <- lapply(intersection.tibble.list, function(ii) {
    ii %>% group_by(drug,cell,measure) %>% filter(n_distinct(experiment) >= opt$min_intersection) %>% ungroup()
  })
```

Plot the distribution of each measure for the intersection.
```{r}
  for (meas in opt$sensitivity_measure) {
    dir.create(file.path(opt$log_dir,meas),showWarnings = FALSE)
    for (comp in names(intersection.tibble.list)) {
      dir.create(file.path(opt$log_dir,meas,comp),showWarnings = FALSE)
      p <- intersection.tibble.list[[comp]] %>%
        filter(measure==meas) %>%
        ggplot(aes(value)) +
          stat_bin(bins=50) + 
          theme_bw() + 
          facet_grid(cols = vars(experiment),rows=vars(drug), scales = 'free_y') + 
          theme(strip.text.x = element_text(size = 12),
            legend.position='none',
            axis.text=element_text(size=12),
            axis.title=element_text(size=12),
            legend.text=element_text(size=12),
            legend.title=element_text(size=12),
            title=element_text(size=14)) +  
        theme(strip.text.x = element_text(size = 8), legend.position="none") + 
          scale_x_continuous(name = meas) 
      ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('densities_raw.pdf',sep='')),width = 12, height = 24, units = "in")
      saveRDS(p, file.path(opt$log_dir,meas,comp,paste('densities_raw.RDS',sep='')))
      p <- intersection.tibble.list[[comp]] %>%
        filter(measure==meas) %>%
        mutate(drug=as.factor(drug)) %>% 
        mutate(drug=reorder(drug, value, mean)) %>%
        mutate(threshold = case_when(drug %in% c('17-AAG','paclitaxel','PD-0325901') ~ .4,
                                     TRUE ~ .2)) %>%
        ggplot(aes(x=value,y=drug,fill=experiment)) +
        geom_density_ridges(alpha = .2) + 
        scale_x_continuous(limits = c(0,1)) + 
        theme_bw() +  scale_fill_brewer(palette="Dark2") +
        theme(axis.title.y = element_blank()) + 
        theme(strip.text.x = element_text(size = 24),
              legend.text=element_text(size=24),
              legend.title=element_text(size=24),
              legend.position="top",
              axis.text=element_text(size=24),
              axis.title = element_text(size=24),
              plot.title = element_text(size = 42),
              plot.subtitle = element_text(size = 32)) +
        labs(x='AAC',title='CCLE and GDSC sensitivity distributions', subtitle= 'Only common drugs shown')
        ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('smoothed_densities_raw.png',sep='')),width = 16, height = 26, units = "in")
        saveRDS(p, file = file.path(opt$log_dir,meas,comp,paste('smoothed_densities_raw.RDS',sep='')))
    }
   p <- intersection.tibble.list[[comp]] %>%
        filter(measure==meas) %>%
        mutate(drug=as.factor(drug)) %>% 
        mutate(drug=reorder(drug, value, mean)) %>%
        ggplot(aes(y=value,x=drug)) +
          geom_boxplot() + 
          theme_bw() + 
          facet_wrap(vars(experiment), scales = 'free_x',ncol=1) + 
            theme(strip.text.x = element_text(size = 18),
            axis.text.x = element_text(angle = 45, hjust = 1),
            legend.position='none',
            axis.text=element_text(size=16),
            axis.title=element_text(size=18),
            legend.text=element_text(size=12),
            legend.title=element_text(size=12),
            title=element_text(size=14)) + 
            scale_y_continuous(breaks=c(0,1)) +
            labs(x="Drug",y=meas)
      ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('boxplot_raw_common_drugs.pdf',sep='')),width = 12, height = 8, units = "in",limitsize=FALSE)
      saveRDS(p, file.path(opt$log_dir,meas,comp,paste('boxplot_raw_common_drugs.RDS',sep='')))
  }
  while(dev.cur()!=1) {dev.off()}
  common.drugs <- lapply(names(intersection.tibble.list), function(comp) {
    intersection.tibble.list[[comp]] %>%
      distinct(drug) %>% 
      pull()
  })
  names(common.drugs) <- names(intersection.tibble.list)
  for (meas in opt$sensitivity_measure) {
    for (comp in names(intersection.tibble.list)) {
      p <- sensitivity.tibble.list[strsplit(comp,split='_')[[1]]] %>%
        bind_rows() %>%
        filter(measure==meas, drug %in% common.drugs[[comp]]) %>%
        mutate(drug=as.factor(drug)) %>% 
        mutate(drug=reorder(drug, value, mean)) %>%
        ggplot(aes(y=value,x=drug,fill=experiment)) +
          geom_boxplot() + 
          theme_bw() + 
          #facet_wrap(vars(experiment), scales = 'free_x',ncol=1) + 
            theme(strip.text.x = element_text(size = 18),
            legend.position='none',
            axis.text=element_text(size=12),
            axis.text.y=element_text(size=16),
            axis.title=element_text(size=18),
            legend.text=element_text(size=12),
            axis.text.x = element_text(angle = 45, hjust = 1),
            legend.title=element_text(size=12),
            title=element_text(size=14)) + 
            scale_y_continuous(breaks=c(0,1)) +
            labs(x="Drug",y=NULL)
      ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('boxplot_raw_all_cells.pdf',sep='')),width = 12, height = 8, units = "in",limitsize=FALSE)
      saveRDS(p, file=file.path(opt$log_dir,meas,comp,paste('boxplot_raw_all_cells.RDS',sep='')))
      maxdr <- sensitivity.tibble.list[strsplit(comp,split='_')[[1]]] %>%
        bind_rows() %>%
        filter(measure==meas, drug %in% common.drugs[[comp]]) %>%
        summarise(max(nchar(drug))) %>%
        pull()
      p <- sensitivity.tibble.list[strsplit(comp,split='_')[[1]]] %>%
        bind_rows() %>%
        filter(measure==meas) %>%
        mutate(color = ifelse(drug %in% common.drugs[[comp]],'blue','grey')) %>%
        mutate(drug=as.factor(drug),color=as.factor(color)) %>% 
        mutate(drug=reorder(drug, value, mean)) %>%
        ggplot(aes(y=value,x=drug)) +
          geom_boxplot(aes(color=color),show.legend=FALSE) + 
          theme_bw() + 
          facet_wrap(vars(experiment), scales = 'free_x',ncol=1) + 
            theme(strip.text.x = element_text(size = 18),
            legend.position='none',
            axis.text=element_text(size=16),
            axis.text.x =element_text(colour = 'white',angle = 45, hjust = 1,size=8),
            axis.title=element_text(size=18),
            legend.text=element_text(size=12),
            legend.title=element_text(size=12),
            title=element_text(size=14)) + 
            labs(x="Drug",y='AAC', title=comp) + 
            scale_y_continuous(breaks=c(0,1)) +
            scale_color_manual(values=c('black','grey50')) 
      ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('boxplot_raw_all_drugs.png',sep='')),width = 12, height = 8, units = "in",limitsize=FALSE)
      saveRDS(p, file=file.path(opt$log_dir,meas,comp,paste('boxplot_raw_all_drugs.RDS',sep='')))
    }
  }
```

Boxplot of all cells.
```{r, eval=FALSE}
sensitivity.tibble.list[['CCLE']] %>%
  bind_rows(sensitivity.tibble.list[['GDSC']]) %>% 
  group_by(drug) %>%
  mutate(numm = n_distinct(experiment)) %>%
  ungroup() %>%
  filter(numm == 2) %>%
  mutate(drug=reorder(drug, value, median)) %>%
  ggplot(aes(x=drug,y=value,fill=experiment)) + 
  geom_boxplot() +  
  theme_bw() + 
  scale_fill_brewer(palette='Dark2') +
  theme(legend.position='bottom',
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x='',y='AAC',subtitle='Only common drugs shown',fill='',title='CCLE and GDSC sensitivity distributions')
```

Repeat for individual studies.
```{r}
  for (meas in opt$sensitivity_measure) {
    dir.create(file.path(opt$log_dir,meas),showWarnings = FALSE)
    for (comp in names(sensitivity.tibble.list)) {
      dir.create(file.path(opt$log_dir,meas,comp),showWarnings = FALSE)
      num_drug <- length(unique(sensitivity.tibble.list[[comp]]$drug))
      p <- sensitivity.tibble.list[[comp]] %>%
        filter(measure==meas) %>%
        ggplot(aes(value)) +
          stat_bin(bins=50) + 
          theme_bw() + 
          facet_wrap(vars(drug), scales = 'free_y',ncol=3) + 
            theme(strip.text.x = element_text(size = 12),
            legend.position='none',
            axis.text=element_text(size=12),
            axis.title=element_text(size=12),
            legend.text=element_text(size=12),
            legend.title=element_text(size=12),
            title=element_text(size=14)) +
          coord_cartesian(xlim = c(0, 1)) +
          scale_x_continuous(name = meas) 
      ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('densities_raw.pdf',sep='')),width = 12, height = num_drug, units = "in",limitsize=FALSE)
      saveRDS(p,file=file.path(opt$log_dir,meas,comp,paste('densities_raw.RDS',sep='')))
      while(dev.cur()!=1) {dev.off()}
      p <- sensitivity.tibble.list[[comp]] %>%
        filter(measure==meas) %>%
        mutate(drug=reorder(drug, value, median)) %>%
        ggplot(aes(x=drug,y=value)) +
          geom_boxplot() + 
          theme_bw() + 
            theme(strip.text.x = element_text(size = 12),
            legend.position='none',
            axis.text=element_text(size=12),
            axis.title=element_text(size=12),
            legend.text=element_text(size=12),
            legend.title=element_text(size=12),
            title=element_text(size=14)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
          coord_cartesian(ylim = c(0, 1)) +
          labs(x='Compound',y='AAC',title=comp)
      if (comp %in% c('GDSC','CTRPv2')) {
        p <- p + theme(axis.text.x =element_blank())
      }
      ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('boxplots_raw.png',sep='')),width = 12, height=6, units = "in")
      saveRDS(p,file=file.path(opt$log_dir,meas,comp,paste('boxplots_raw.RDS',sep='')))
    }
  }
  while(dev.cur()!=1) {dev.off()}
```

Random plots for presentations.
```{r, eval=FALSE}
comp <- 'CCLE'
dr <- 'Irinotecan'
p <- sensitivity.tibble.list[[comp]] %>%
        filter(measure==meas,drug==dr) %>%
        ggplot(aes(value)) +
          stat_bin() + 
          theme_bw() + 
            theme(strip.text.x = element_text(size = 12),
            legend.position='none',
            axis.text=element_text(size=12),
            axis.title=element_text(size=12),
            legend.text=element_text(size=12),
            legend.title=element_text(size=12),
            title=element_text(size=14)) +
          coord_cartesian(xlim = c(0, 1)) +
  labs(x='AAC',y='Count',title='Distribution of drug sensitivity', subtitle='CCLE - Compound: Irinotecan')
      ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('myfigure.pdf',sep='')),width = 8, height = 6, units = "in",limitsize=FALSE)

```

Plot the pairwise concordance between two studies at a time.
```{r}
  for (meas in opt$sensitivity_measure) {
    for (comp in names(intersection.tibble.list)) {
      combos <- t(combn(sort(unique(intersection.tibble.list[[comp]]$experiment)),2))
      for (combo in 1:nrow(combos)) {
        p <- intersection.tibble.list[[comp]] %>%
          filter(experiment %in% combos[combo,],
                 measure == meas) %>%
          select(drug,cell,experiment, measure, everything()) %>%
          gather(variable, value, -(drug:measure)) %>% 
          unite(temp, experiment, variable) %>%
          spread(temp,value) %>%
          ggplot(aes_string(x=paste(combos[combo,1],'value',sep='_'),
                            y=paste(combos[combo,2],'value',sep='_'))) + 
          geom_point(alpha=.15,size=1.5) + 
          scale_color_brewer(palette = 'Dark2') + 
          geom_abline(slope=1, size=.5,color='black', lty=3) + 
          theme_bw() + 
          facet_wrap(vars(drug),ncol=5) + 
          theme(strip.text.x = element_text(size = 12),
            legend.position='top',
            axis.text=element_text(size=12),
            axis.title=element_text(size=12),
            legend.text=element_text(size=12),
            legend.title=element_text(size=0),
            title=element_text(size=14)) +
          labs(x=combos[combo,1], y=combos[combo,2]) + 
          scale_x_continuous(breaks=c(0,.5,1),labels=c('0','0.5','1'),limits = c(0,1)) +
          scale_y_continuous(breaks=c(0,.5,1),labels=c('0','0.5','1'),limits = c(0,1))
        ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('2way_',
                                              combos[combo,1],'_',combos[combo,2],
                                              '.pdf',sep='')),
             width = 18, height = 10, units = "in")
        saveRDS(p,file=file.path(opt$log_dir,meas,comp,paste('2way_',
                                              combos[combo,1],'_',combos[combo,2],
                                              '.RDS',sep='')))
        drugs <- unique(intersection.tibble.list[[comp]]$drug)
        dir.create(file.path(opt$log_dir,meas,comp,'by_drug'),showWarnings = FALSE)
        for (dr in drugs) {
          p <- intersection.tibble.list[[comp]] %>%
          filter(experiment %in% combos[combo,],drug==dr,measure==meas) %>% 
          select(drug,cell,experiment, measure, everything()) %>%
          gather(variable, value, -(drug:measure)) %>% 
          unite(temp, experiment, variable) %>%
          spread(temp,value) %>%
          #mutate(CCLE_value = (CCLE_value-mean(CCLE_value))/sd(CCLE_value),
          #       GDSC_value = (GDSC_value-mean(GDSC_value))/sd(GDSC_value)) %>%
          ggplot(aes_string(x=paste(combos[combo,1],'value',sep='_'),
                            y=paste(combos[combo,2],'value',sep='_'))) + 
          geom_point(alpha=.5,size=4) + 
          #geom_smooth(method='lm',se=FALSE) +
          scale_color_brewer(palette = 'Dark2') + 
          theme_bw() + 
          theme(strip.text.x = element_text(size = 12),
              legend.position='top',
              axis.text=element_text(size=16),
              axis.title=element_text(size=16),
              legend.text=element_text(size=22),
              legend.title=element_text(size=0),
              title=element_text(size=14)) +
          labs(x=combos[combo,1],y=combos[combo,2],title=paste(dr,' common cell sensitivity (AAC)',sep='')) + 
          scale_x_continuous(breaks=c(0,.5,1),labels=c('0','0.5','1'),limits = c(0,1)) +
          scale_y_continuous(breaks=c(0,.5,1),labels=c('0','0.5','1'),limits = c(0,1))
        ggsave(p,file=file.path(opt$log_dir,meas,comp,'by_drug',paste(dr,'_2way_',
                                                combos[combo,1],'_',combos[combo,2],
                                                '.png',sep='')),
               width = 10, height = 8, units = "in")
        saveRDS(p,file.path(opt$log_dir,meas,comp,'by_drug',paste(dr,'_2way_',
                                                combos[combo,1],'_',combos[combo,2],
                                                '.RDS',sep='')))
        }
      }
    }
  }
```

Initialize drug and cell assignments for EM using prior specifications for probability sensitive and probability drug is broadly active.
```{r}
drugs.tibble.list <- lapply(sensitivity.tibble.list, function(li) {
  drug_dat <- li %>% 
    mutate(all_median = quantile(value,opt$prior.sensitive),
           all_mad = stats::mad(value),
           drug=as.factor(drug)) %>% 
    group_by(drug) %>% 
    mutate(median=median(value),
           mad=stats::mad(value),
           all_median=first(all_median),
           all_mad=first(all_mad)) %>%
    ungroup() %>%
    mutate(drug_type = ifelse(median<=all_median & mad<=all_mad,'targeted','broad')) %>%
    distinct(drug, drug_type, all_median, all_mad, median, median, mad)
  li %>% 
    left_join(drug_dat, by='drug') %>%
    mutate(sensitive = ifelse(value > all_median, 1,0)) %>%
    group_by(drug, measure, drug_type) %>%
    summarise(p_prior = mean(sensitive),
              sensitive = sum(sensitive),
              cell_count = n()) %>%
    ungroup() %>% 
    select(drug, measure, p_prior, sensitive, cell_count, drug_type)
})
cells.tibble.list <- lapply(1:length(sensitivity.tibble.list), function(li) {
  sensitivity.tibble.list[[li]] %>% 
    left_join(drugs.tibble.list[[li]], by=c('drug','measure')) %>% 
    select(drug:measure,drug_type) %>%
    mutate(thresho = case_when(drug_type == 'broad' ~ .5, TRUE ~ .95)) %>%
    group_by(drug) %>%
    mutate(cell_type = ifelse(value>=quantile(value,probs = thresho),'sensitive','resistant')) %>%
    ungroup() %>% 
    select(-thresho)
})
names(cells.tibble.list) <- names(drugs.tibble.list)
```

Plot median versus median absolute deviation for joined data using the MAD and specified percentile for drug-type classification.
```{r}
library(ggrepel)
  for (meas in opt$sensitivity_measure) {
    for (comp in names(sensitivity.tibble.list)) {
      p <- sensitivity.tibble.list[[comp]] %>%
        filter(measure==meas) %>%
        mutate(all_median = quantile(value,.6),
               all_mad = stats::mad(value),
               drug=as.factor(drug)) %>% 
        group_by(drug) %>% 
        summarise(median=median(value),
                  mad=stats::mad(value),
                  all_median=first(all_median),
                  all_mad=first(all_mad)) %>%
        mutate(broad = ifelse(median<=all_median & mad<=all_mad,'Narrow effect','Broad effect'),
               broad_hk = ifelse(mad>.13,'Broad effect','Narrow effect')) %>%
        ggplot(aes(x=median,y=mad)) + 
        geom_point(aes(color=broad),size=4,alpha=.6,show.legend=FALSE) +
        #geom_hline(aes(yintercept=.13),lty=2,color=2) + 
        geom_hline(aes(yintercept=all_mad),lty=2) + 
        geom_vline(aes(xintercept=all_median),lty=2) +
        theme_bw() +
        labs(x='Median AAC', y='Median absolute deviation (MAD)') + 
        ggtitle(comp)
      ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Median_v_MAD.pdf',sep='')),width = 5, height = 5, units = "in",limitsize=FALSE)
      saveRDS(p, file=file.path(opt$log_dir,meas,comp,paste('Median_v_MAD.RDS',sep='')))
    }
  }
  for (meas in opt$sensitivity_measure) {
    for (comp in names(intersection.tibble.list)) {
      combos <- t(combn(sort(unique(intersection.tibble.list[[comp]]$experiment)),2))
      for (combo in 1:nrow(combos)) {
        study1 <- sensitivity.tibble.list[[combos[combo,1]]] %>%
          filter(measure==meas) %>%
          mutate(all_median = quantile(value,.6),
                 all_mad = stats::mad(value),
                 drug=as.factor(drug)) %>% 
          group_by(drug) %>% 
          summarise(median=median(value),
                    mad=stats::mad(value),
                    all_median=first(all_median),
                    all_mad=first(all_mad)) %>%
          mutate(broad = ifelse(median<=all_median & mad<=all_mad,'Narrow effect','Broad effect'),
                 broad_hk = ifelse(mad>.13,'Broad effect','Narrow effect'))
        study2 <- sensitivity.tibble.list[[combos[combo,2]]] %>%
          filter(measure==meas) %>%
          mutate(all_median = quantile(value,.6),
                 all_mad = stats::mad(value),
                 drug=as.factor(drug)) %>% 
          group_by(drug) %>% 
          summarise(median=median(value),
                    mad=stats::mad(value),
                    all_median=first(all_median),
                    all_mad=first(all_mad)) %>%
          mutate(broad = ifelse(median<=all_median & mad<=all_mad,'Narrow effect','Broad effect'),
               broad_hk = ifelse(mad>.13,'Broad effect','Narrow effect'))
        studies <- study1 %>% mutate(experiment=combos[combo,1]) %>% 
          bind_rows(study2 %>% mutate(experiment=combos[combo,2]))
        p <- intersection.tibble.list[[comp]] %>%
          filter(experiment %in% combos[combo,],
                 measure == meas) %>%
          distinct(drug,experiment) %>%
          left_join(studies,by=c('drug','experiment')) %>%
          ggplot(aes(x=median,y=mad,color=broad,shape=broad_hk,label=drug),size=3) + 
          geom_point() +
          geom_hline(aes(yintercept=.13),lty=2,color=2) + 
          geom_hline(aes(yintercept=all_mad),lty=2) + 
          geom_vline(aes(xintercept=all_median),lty=2) +
          theme_bw() +
          facet_grid(cols=vars(experiment)) + 
          scale_color_brewer(palette='Dark2') +
          geom_text_repel(show.legend=FALSE,size=5)
        ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Median_v_MAD.pdf',sep='')),width = 8, height = 5, units = "in",limitsize=FALSE)
        saveRDS(p, file=file.path(opt$log_dir,meas,comp,paste('Median_v_MAD.RDS',sep='')))
      }
    }
  }
```

Plot the drug and cell initial assignments.
```{r}
library(ggrepel)
  for (meas in opt$sensitivity_measure) {
    for (comp in names(sensitivity.tibble.list)) {
      p <- drugs.tibble.list[[comp]] %>%
        filter(measure==meas) %>%
        ggplot(aes(p_prior)) +
          stat_bin(bins=50) + 
          theme_bw() + 
          theme(strip.text.x = element_text(size = 12),
            legend.position='none',
            axis.text=element_text(size=12),
            axis.title=element_text(size=12),
            legend.text=element_text(size=12),
            legend.title=element_text(size=12),
            title=element_text(size=14)) +
          coord_cartesian(xlim = c(0, 1)) +
          scale_x_continuous(name = 'p_prior') 
      ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('p_prior.pdf',sep='')),width = 4, height = 4, units = "in",limitsize=FALSE)
      saveRDS(p, file=file.path(opt$log_dir,meas,comp,paste('p_prior.RDS',sep='')))
    }
  }
  for (meas in opt$sensitivity_measure) {
    for (comp in names(intersection.tibble.list)) {
      p <-  cells.tibble.list[strsplit(comp,split='_')[[1]]] %>%
        bind_rows() %>%
        filter(measure==meas, drug %in% common.drugs[[comp]]) %>%
        mutate(drug=as.factor(drug)) %>% 
        mutate(drug=reorder(drug, value, mean)) %>%
        ggplot(aes(y=value,x=drug,fill=as.factor(drug_type))) +
          geom_boxplot() + 
          theme_bw() + 
          facet_wrap(vars(experiment), scales = 'free_x',ncol=1) + 
            theme(strip.text.x = element_text(size = 18),
            legend.position='bottom',
            axis.text=element_text(size=12),
            axis.text.y=element_text(size=16),
            axis.title=element_text(size=18),
            legend.text=element_text(size=12),
            axis.text.x = element_text(angle = 45, hjust = 1),
            legend.title=element_text(size=12),
            title=element_text(size=14)) + 
            scale_y_continuous(breaks=c(0,1)) +
            labs(x="Drug",y=NULL)
      ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('boxplot_raw_all_cells_prior.pdf',sep='')),width = 12, height = 8, units = "in",limitsize=FALSE)
      saveRDS(p, file=file.path(opt$log_dir,meas,comp,paste('boxplot_raw_all_cells_prior.RDS',sep='')))
      maxdr <- sensitivity.tibble.list[strsplit(comp,split='_')[[1]]] %>%
        bind_rows() %>%
        filter(measure==meas, drug %in% common.drugs[[comp]]) %>%
        summarise(max(nchar(drug))) %>%
        pull()
      p <- cells.tibble.list[strsplit(comp,split='_')[[1]]] %>%
        bind_rows() %>%
        filter(measure==meas) %>%
        mutate(color = ifelse(drug %in% common.drugs[[comp]],'blue','grey')) %>%
        mutate(drug=as.factor(drug),color=as.factor(color)) %>% 
        mutate(drug=reorder(drug, value, mean)) %>%
        ggplot(aes(y=value,x=drug)) +
          geom_boxplot(aes(color=color, fill=as.factor(drug_type)),show.legend=FALSE) + 
          theme_bw() + 
          facet_wrap(vars(experiment), scales = 'free_x',ncol=1) + 
            theme(strip.text.x = element_text(size = 18),
            legend.position='bottom',
            axis.text=element_text(size=16),
            axis.text.x =element_text(colour = 'white',angle = 45, hjust = 1,size=8),
            axis.title=element_text(size=18),
            legend.text=element_text(size=12),
            legend.title=element_text(size=12),
            title=element_text(size=14)) + 
            labs(x="Drug",y=meas) + 
            scale_y_continuous(breaks=c(0,1)) +
            scale_color_manual(values=c('black','grey50')) 
      ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('boxplot_raw_all_drugs_prior.pdf',sep='')),width = 12, height = 8, units = "in",limitsize=FALSE)
      saveRDS(p, file=file.path(opt$log_dir,meas,comp,paste('boxplot_raw_all_drugs_prior.RDS',sep='')))
    }
  }
```

Smoothed density of the prior pi across all studies.
```{r}
  for (meas in opt$sensitivity_measure) {
    temptibb <- tibble()
    for (comp in names(sensitivity.tibble.list)) {
      temptibb <- drugs.tibble.list[[comp]] %>%
        filter(measure==meas) %>%
        mutate(experiment=comp) %>%
        bind_rows(temptibb)
    }
    p <- temptibb %>% 
      ggplot(aes(x=p_prior,fill='one',y=..scaled..)) +
        geom_density(alpha = .5) + 
        theme_bw() +  
        facet_wrap(vars(experiment),nrow=2) +
        scale_fill_brewer(palette="Dark2") +
        theme(strip.text.x = element_text(size = 14),
              legend.text=element_text(size=14),
              legend.title=element_text(size=14),
              legend.position="none",
              axis.text=element_text(size=12),
              axis.title = element_text(size=14),
              plot.title = element_text(size = 16)) +
        scale_x_continuous(breaks=c(0,.5,1),labels=c('0','0.5','1'),limits = c(0,1),name=expression(paste(p, '(',pi, ")",sep=''))) +
        scale_y_continuous(breaks=c(0,1),labels=c('0','1'),limits = c(0,1), name='Density')
    ggsave(p, file=file.path(opt$log_dir,meas,paste('p_prior_smoothed.pdf',sep='')),width = 4, height = 4, units = "in",limitsize=FALSE)
    saveRDS(p, file=file.path(opt$log_dir,meas,paste('p_prior_smoothed.RDS',sep='')))
  }
```

Using the assignments, fit distributions (first M step) and use these as priors to initialize EM with. 
```{r}
meas <- opt$sensitivity_measure[1]
drug_types_list <- lapply(drugs.tibble.list, function(tibb) {
  tibb %>%
    filter(measure==meas) %>%
    group_by(drug_type) %>%
    do(mutate(fit_bb_mle(.$sensitive, .$cell_count), number = nrow(.))) %>%
    ungroup() %>%
    mutate(drug_type_prior = number / sum(number))
})
targetted_drug_fits_list <- lapply(cells.tibble.list, function(tibb) {
  ttibb <- tibb %>%
    filter(measure==meas) %>%
    mutate(value = ifelse(value==0,1e-3,value)) %>%
    mutate(drug_type = 'targeted') %>%
    group_by(drug, cell_type, drug_type) %>%
    do(mutate(fit_beta_mle(.$value),number = nrow(.))) %>%
    group_by(drug, drug_type) %>%
    mutate(ndist=n_distinct(cell_type)) %>%
    ungroup()
  ttibb %>%
    bind_rows(
      ttibb %>% 
        filter(ndist<2) %>% 
        mutate(cell_type2 = case_when(cell_type=='resistant' ~ 'sensitive',cell_type=='sensitive' ~ 'resistant'),
               cell_type=cell_type2,
               number=0,
               alpha=case_when(cell_type == 'resistant' ~ 1,
                               cell_type == 'sensitive' ~ 1),
               beta=case_when(cell_type == 'resistant' ~ 1,
                              cell_type == 'sensitive' ~ 1)) %>%
        select(-cell_type2)
    ) %>%
    group_by(drug) %>%       
    mutate(targeted_cell_type_prior = number / sum(number)) %>%
    ungroup() %>% 
    select(-ndist)
})
broad_drug_fits_list <- lapply(cells.tibble.list, function(tibb) {
  tibb %>%
    filter(measure==meas) %>%
    mutate(x=ifelse(value==0,1e-3,value)) %>%
    group_by(drug) %>%
    do(mutate(fit_beta_mle(.$x),number = nrow(.))) %>%
    ungroup() %>% 
    mutate(broad_cell_type_prior = .5, drug_type = 'broad') %>% 
    select(drug, drug_type, alpha, beta, number, broad_cell_type_prior)
})
```

Perform an expectation step using the distributions to initialize for the EM. 
```{r}
targetted_cell_assignments_list <- lapply(1:length(targetted_drug_fits_list), function(num) {
  targetted_drug_list <- unique(targetted_drug_fits_list[[num]]$drug)
  targetted_cell_assignments <- lapply(targetted_drug_list, function(dr) {
    cells.tibble.list[[num]] %>%
      filter(drug == dr,measure==meas) %>%
      select(drug:measure) %>%
      mutate(drug_type = 'targeted') %>%
      mutate(value=ifelse(value==0,1e-3,value)) %>%
      crossing(targetted_drug_fits_list[[num]] %>% filter(drug == dr) %>% select(-drug,-drug_type)) %>%
      mutate(median = qbeta(.5,alpha,beta),
             likelihood = dbeta(value, alpha, beta)) %>% 
      group_by(cell_type) %>%
      mutate(max.likelihood=max(likelihood)) %>%
      ungroup() %>%
      mutate(likelihood = case_when(value>median & cell_type == 'sensitive' ~ max.likelihood-likelihood + max.likelihood, 
                                    TRUE~likelihood)) %>%
      mutate(likelihood = targeted_cell_type_prior * likelihood) %>%
      group_by(drug, cell) %>%
      mutate(posterior=exp(log(likelihood)-log(sum(likelihood)))) %>% 
      top_n(1, likelihood) %>%
      ungroup()
  })
  do.call(bind_rows, targetted_cell_assignments)
})
broad_cell_assignments_list <- lapply(1:length(broad_drug_fits_list), function(num) {
  cells.tibble.list[[num]] %>%
      filter(drug %in% unique(broad_drug_fits_list[[num]]$drug),measure==meas) %>%
      select(drug:measure) %>%
      mutate(drug_type = 'broad') %>%
      mutate(value=ifelse(value==0,1e-3,value)) %>%
      left_join(broad_drug_fits_list[[num]], by=c('drug','drug_type')) %>%
      mutate(likelihood = 1 * dbeta(value, alpha, beta),
             cell_type = ifelse(value>=qbeta(.5,.$alpha,.$beta),'sensitive','resistant'))
})

drugs.tibble.list <- lapply(1:length(drugs.tibble.list), function(num) {
  targetteds <- drugs.tibble.list[[num]] %>%
    filter(measure==meas) %>%
    select(drug, measure, p_prior) %>%
    right_join(targetted_cell_assignments_list[[num]] %>% select(drug, cell, cell_type, likelihood), by='drug') %>% 
    group_by(drug, measure, p_prior) %>%
    summarise(sensitive = sum(cell_type=='sensitive'),
              cell_count = n()) %>%
    ungroup() %>% 
    mutate(type='targeted')
  broads <- drugs.tibble.list[[num]] %>%
    filter(measure==meas) %>%
    select(drug, measure, p_prior) %>%
    right_join(broad_cell_assignments_list[[num]] %>% select(drug, cell, cell_type), by='drug') %>% 
    group_by(drug, measure, p_prior) %>%
    summarise(sensitive = sum(cell_type=='sensitive'),
              cell_count = n()) %>%
    ungroup() %>%
    mutate(type='broad')
  bind_rows(targetteds, broads)
})

drug_assignments_list <- lapply(1:length(drugs.tibble.list), function(num) {
  drugs.tibble.list[[num]] %>%
    filter(measure==meas) %>%
    rename(drug_type = type) %>%
    right_join(drug_types_list[[num]] %>% select(-number, -drug_type_prior), by='drug_type') %>%
    mutate(drug_type_prior = case_when (drug_type == 'broad' ~ p_prior, TRUE ~ 1-p_prior)) %>%
    mutate(likelihood = drug_type_prior * VGAM::dbetabinom.ab(sensitive, cell_count, alpha, beta)) %>%
    group_by(drug) %>%
    mutate(posterior=likelihood/sum(likelihood)) %>% 
    top_n(1, likelihood) %>%
    ungroup()
})

cell_assignments_list <- lapply(1:length(targetted_cell_assignments_list), function(num) {
  bind_rows(targetted_cell_assignments_list[[num]],broad_cell_assignments_list[[num]]) %>%
    group_by(drug, cell_type) %>%
    fill(targeted_cell_type_prior, .direction='down') %>%
    ungroup() %>%
    group_by(drug) %>% 
    fill(broad_cell_type_prior, .direction='up') %>%
    ungroup() %>% 
    right_join(drug_assignments_list[[num]] %>% select(drug, drug_type), by=c('drug','drug_type')) %>% 
    select(drug, cell, value, experiment, measure, drug_type, cell_type, broad_cell_type_prior, targeted_cell_type_prior)
})
names(cell_assignments_list) <- names(drug_types_list)
```

Plot the prior drug densities.
```{r, eval=FALSE}  
for (num in names(drug_types_list)) {
  drug_type_iterations <- drug_types_list[[num]]
  drug_fits_iterations <- bind_rows(broad_drug_fits_list[[num]],targetted_drug_fits_list[[num]])
  cell_assignments_iterations <- cell_assignments_list[[num]]
  betadens <- drug_fits_iterations %>%
    mutate(cross = paste(cell_type, drug, sep='_')) %>%
    plyr::ddply(., "cross", function(df) {
      data.frame( 
      value = seq(.001, .999, length = 1000),
      beta_curve = dbeta(seq(.001, .999, length = 1000), 
                           df$alpha, 
                           df$beta) 
    )
  })
  betadens <- as_tibble(betadens) %>% 
    separate(cross,into=c('cell_type','drug'),sep='_') %>%
    full_join(drug_fits_iterations %>% mutate(cell_type = ifelse(is.na(cell_type),'NA',cell_type)), by=c('drug','cell_type')) %>%
    group_by(drug,cell_type) %>% 
    mutate(prior = ifelse(prior < .1,.1,prior)) %>%
    mutate(beta_curve = beta_curve/max(beta_curve)*prior) %>%
    ungroup() %>%
    filter(beta_curve>1e-5) %>%
    mutate(cell_type = ifelse(cell_type=='sensitive','sensitive','resistant'))
  p <- cell_assignments_iterations %>%
    ggplot(aes(value,y=..scaled..)) +
      geom_density(adjust=.5,fill=1) +
      theme_bw() + 
      facet_wrap(vars(drug), scales = 'free_y',ncol=3) + 
      theme(strip.text.x = element_text(size = 8),
          legend.position='none',
          axis.text=element_text(size=12),
          axis.title=element_text(size=12),
          legend.text=element_text(size=12),
          legend.title=element_text(size=12),
          title=element_text(size=14)) + 
    scale_x_continuous(limits = c(0,1), name=meas) + 
    geom_line(data=betadens, aes(y = beta_curve, color=cell_type), lwd = 1) 
  ggsave(p,file=file.path(opt$log_dir,meas,num,paste('prior_densities_smoothed.pdf',sep='')),width = 12, height = 24, units = "in")
  saveRDS(p, file=file.path(opt$log_dir,meas,num,paste('prior_densities_smoothed.RDS',sep='')))
  while(dev.cur()!=1) {dev.off()}
  dir.create(file.path(opt$log_dir,meas,num,'prior_densities_by_drug'),showWarnings = FALSE)
  for (dr in unique(cell_assignments_iterations$drug)) {
    dr_type <- cell_assignments_iterations %>%
      filter(drug==dr) %>% 
      distinct(drug_type) %>% 
      pull
    dr_short <- gsub("[^[:alnum:]]","",dr)
    dr_nonums <- gsub('[0-9]+', '', dr_short)
    if (nchar(dr_nonums)==0) {dr_short <- paste('drug',dr_short,sep='')}
    p <- cell_assignments_iterations %>%
      filter(drug==dr) %>%
      ggplot(aes(value,y=..scaled..)) +
        geom_density(adjust=.5,fill=1) +
        theme_bw() + 
        theme(strip.text.x = element_text(size = 18),
          legend.position='none',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=16),
          title=element_text(size=18)) +
      scale_x_continuous(limits = c(0,1)) + 
      labs(y='Scaled Density',x='AOC') +
      geom_line(data=betadens %>% filter(drug==dr), aes(y = beta_curve, color=cell_type), lwd = 1.5) +
      ggtitle(paste(dr,sep=' '))
    ggsave(p, file=file.path(opt$log_dir,meas,num,'prior_densities_by_drug',paste(dr_short,'.png',sep='')),width = 12, height = 8, units = "in")
    saveRDS(p, file=file.path(opt$log_dir,meas,num,'prior_densities_by_drug',paste(dr_short,'.RDS',sep='')))
  }
}
```

Run EM.
```{r}
  iterations_list <- list()
  for(num in 1:length(cell_assignments_list)) {
    drug_assignments <- drug_assignments_list[[num]]
    cell_assignments <- cell_assignments_list[[num]]
    iterations_list[[num]] <- accumulate(1:3, iterate_em, .init = list(drug_assignments = drug_assignments,
                                                                       cell_assignments = cell_assignments))
  }
  names(iterations_list) <- names(sensitivity.tibble.list)
```

Plot parameters across iterations.
```{r}
for (num in names(iterations_list)) {
  drug_type_iterations <- iterations_list[[num]] %>% 
    map_df("drug_types", .id = "iteration") %>% 
    bind_rows(drug_types_list[[num]] %>% 
                mutate(iteration='0')) %>%
    group_by(iteration) %>%
    mutate(drug_type_prior = case_when(is.na(drug_type_prior) ~ number/sum(number), TRUE ~ drug_type_prior)) %>%
    ungroup()
  drug_fits_iterations <- iterations_list[[num]] %>% 
    map_df("drug_fits", .id = "iteration") %>% 
    bind_rows(broad_drug_fits_list[[num]] %>% 
                mutate(iteration='0') %>%
                select(drug, drug_type, alpha, beta, iteration),
              targetted_drug_fits_list[[num]] %>% 
                mutate(iteration='0') %>%
                select(drug, drug_type, alpha, beta, iteration))
  cell_assignments_iterations <- iterations_list[[num]] %>% 
    map_df("cell_assignments", .id = "iteration") %>% 
    bind_rows(cell_assignments_list[[num]] %>%
                mutate(iteration='0'))
  p <- drug_type_iterations %>%
    crossing(x = seq(.001, .999, .001)) %>%
    mutate(density = drug_type_prior * dbeta(x, alpha, beta)) %>%
    ggplot(aes(x, density, color = iteration, group = iteration)) +
    geom_line() +
    facet_wrap(~ drug_type) + 
    theme(strip.text.x = element_text(size = 18),
          legend.position='bottom',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=16),
          title=element_text(size=18)) +
          labs(y='Density',x='AOC')
  ggsave(p,file=file.path(opt$log_dir,meas,num,paste('parameter_updates.pdf',sep='')),width = 12, height = 8, units = "in")
  saveRDS(p,file=file.path(opt$log_dir,meas,num,paste('parameter_updates.RDS',sep='')))
}
```

Obtain posterior information from last EM rep.
```{r}
  posterior_drug_types_list <- lapply(names(iterations_list), function(num) {
    iterations_list[[num]] %>% 
      map_df("drug_types", .id = "iteration") %>% 
      filter(iteration==max(iteration))
  })
  posterior_drug_assignments_list <- lapply(names(iterations_list), function(num) {
    iterations_list[[num]] %>% 
      map_df("drug_assignments", .id = "iteration") %>% 
      filter(iteration==max(iteration))
  })
  posterior_drug_fits_list <- lapply(names(iterations_list), function(num) {
    iterations_list[[num]] %>% 
      map_df("drug_fits", .id = "iteration") %>% 
      filter(iteration==max(iteration))
  })
  posterior_cell_assignments_list <- lapply(names(iterations_list), function(num) {
    iterations_list[[num]] %>% 
      map_df("cell_assignments", .id = "iteration") %>% 
      filter(iteration==max(iteration))
  })
  names(posterior_cell_assignments_list) <- names(iterations_list)
```

Plot the posterior drug densities.
```{r}  
drug_posteriors_proportions <- lapply(names(posterior_cell_assignments_list), function(ii) {
  posterior_cell_assignments_list[[ii]] %>%
    group_by(drug) %>%
    summarise(posterior = sum(cell_type=='sensitive')/n()) %>%
    ungroup()
}) 
names(drug_posteriors_proportions) <- names(iterations_list)
for (num in names(iterations_list)) {
  drug_type_iterations <- iterations_list[[num]] %>% 
    map_df("drug_types", .id = "iteration") %>% 
    bind_rows(drug_types_list[[num]] %>% 
                mutate(iteration='0')) %>%
    group_by(iteration) %>%
    mutate(drug_type_prior = case_when(is.na(drug_type_prior) ~ number/sum(number), TRUE ~ drug_type_prior)) %>%
    ungroup()
  drug_fits_iterations <- iterations_list[[num]] %>% 
    map_df("drug_fits", .id = "iteration") %>% 
    bind_rows(broad_drug_fits_list[[num]] %>% 
                mutate(iteration='0') %>%
                select(drug, drug_type, alpha, beta, iteration),
              targetted_drug_fits_list[[num]] %>% 
                mutate(iteration='0') %>%
                select(drug, drug_type, alpha, beta, iteration))
  cell_assignments_iterations <- iterations_list[[num]] %>% 
    map_df("cell_assignments", .id = "iteration") %>% 
    bind_rows(cell_assignments_list[[num]] %>%
                mutate(iteration='0'))
  betadens <- drug_fits_iterations %>%
    filter(iteration==max(iteration)) %>%
    mutate(cross = paste(cell_type, drug, sep='_')) %>%
    plyr::ddply(., "cross", function(df) {
      data.frame( 
      value = seq(.001, .999, length = 1000),
      beta_curve = dbeta(seq(.001, .999, length = 1000), 
                           df$alpha, 
                           df$beta) 
    )
  })
  betadens <- as_tibble(betadens) %>% 
    separate(cross,into=c('cell_type','drug'),sep='_') %>%
    full_join(drug_fits_iterations %>% mutate(cell_type = ifelse(is.na(cell_type),'NA',cell_type)), by=c('drug','cell_type')) %>% 
    left_join(drug_posteriors_proportions[[num]], by='drug') %>%
    mutate(posterior = ifelse(drug_type=='broad',1,posterior)) %>%
    mutate(posterior = ifelse(drug_type=='targeted' & cell_type=='resistant',1,posterior)) %>%
    group_by(drug,cell_type) %>% 
    #mutate(prior = ifelse(prior < .1,.1,prior)) %>%
    mutate(beta_curve = beta_curve/max(beta_curve)*posterior) %>%
    ungroup() %>%
    filter(iteration==max(iteration)) %>%
    mutate(cell_type = ifelse(cell_type=='sensitive','sensitive','resistant'))
  nummdrs <- betadens %>% summarise(n_distinct(drug)) %>% pull()
  drs_array <- betadens %>% distinct(drug) %>% pull()
  seeqq <- seq(1,nummdrs,by=16)
  for (dr_chunk in 1:length(seeqq)) {
    p <- cell_assignments_iterations %>%
      filter(iteration==max(iteration)) %>%
      filter(drug %in% drs_array[seeqq[dr_chunk]:(seeqq[dr_chunk]+15)]) %>%
      ggplot(aes(value,y=..scaled..)) +
        geom_density(adjust=.5,fill=1) +
        theme_bw() + 
        facet_wrap(vars(drug), scales = 'free_y',ncol=4) + 
        theme(strip.text.x = element_text(size = 8),
            legend.position='none',
            axis.text=element_text(size=12),
            axis.title=element_text(size=12),
            legend.text=element_text(size=12),
            legend.title=element_text(size=12),
            title=element_text(size=14)) + 
      scale_x_continuous(limits = c(0,1), name=meas) + 
      geom_line(data=betadens %>% filter(drug %in% drs_array[seeqq[dr_chunk]:(seeqq[dr_chunk]+15)]), aes(y = beta_curve, color=cell_type), lwd = 1) 
    ggsave(p, file=file.path(opt$log_dir,meas,num,paste('fitted_densities_smoothed_',dr_chunk,'.pdf',sep='')),width = 12, height = 24, units = "in")
    saveRDS(p, file=file.path(opt$log_dir,meas,num,paste('fitted_densities_smoothed_',dr_chunk,'.RDS',sep='')))
    while(dev.cur()!=1) {dev.off()}
  }
  dir.create(file.path(opt$log_dir,meas,num,'fitted_densities_by_drug'),showWarnings = FALSE)
  for (dr in unique(cell_assignments_iterations$drug)) {
    dr_type <- cell_assignments_iterations %>%
      filter(iteration==max(iteration),drug==dr) %>% 
      distinct(drug_type) %>% 
      pull
    dr_short <- gsub("[^[:alnum:]]","",dr)
    dr_nonums <- gsub('[0-9]+', '', dr_short)
    if (nchar(dr_nonums)==0) {dr_short <- paste('drug',dr_short,sep='')}
    p <- cell_assignments_iterations %>%
      filter(iteration==max(iteration),drug==dr) %>%
      ggplot(aes(value,y=..scaled..)) +
        geom_density(adjust=.5,fill=1) +
        theme_bw() + 
        theme(strip.text.x = element_text(size = 18),
          legend.position='none',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=16),
          title=element_text(size=18)) +
      scale_x_continuous(limits = c(0,1)) + 
      labs(y='Scaled Density',x='AOC') +
      geom_line(data=betadens %>% filter(drug==dr), aes(y = beta_curve, color=cell_type), lwd = 1.5) +
      ggtitle(paste(dr,sep=' '))
    ggsave(file=file.path(opt$log_dir,meas,num,'fitted_densities_by_drug',paste(dr_short,'.png',sep='')),width = 12, height = 4, units = "in")
    saveRDS(p, file.path(opt$log_dir,meas,num,'fitted_densities_by_drug',paste(dr_short,'.RDS',sep='')))
  }
}
```

Extract intersection data.
```{r}
  intersection.fitted.list <- lapply(intersection.tibble.list, function(tibb) {
    drugs_cells <- tibb %>% 
      distinct(drug,cell)
    experiments <- tibb %>% 
      distinct(experiment) %>%
      pull
    newtibb <- NULL
    for (exp in experiments) {
      iter <- iterations_list[[exp]] %>% 
        map_df("cell_assignments", .id = "iteration") %>%
        filter(iteration == max(iteration))
      newtibb <- bind_rows(newtibb,drugs_cells %>% 
        left_join(iter, by=c('drug','cell')))
    }
    return(newtibb)
  })
```

Format posterior agreements.
```{r}
  posterior_drug_types <- do.call(bind_rows,posterior_drug_types_list) %>%
    mutate(experiment=rep(names(iterations_list),each=2)) 
  nums <- sapply(posterior_drug_assignments_list, nrow)
  posterior_drug_assignments <- do.call(bind_rows,posterior_drug_assignments_list) %>%
      mutate(experiment=rep(names(iterations_list),times=nums))
  nums <- sapply(posterior_drug_fits_list, nrow)
  posterior_drug_fits <-  do.call(bind_rows,posterior_drug_fits_list) %>%
      mutate(experiment=rep(names(iterations_list),times=nums))
  nums <- sapply(posterior_cell_assignments_list, nrow)
  posterior_cell_assignments <- do.call(bind_rows,posterior_cell_assignments_list) %>%
      mutate(experiment=rep(names(iterations_list),times=nums))
```

Save posteriors.
```{r}
saveRDS(object=posterior_drug_types,file=file.path(opt$log_dir,'posterior_drug_types.RDS'))
saveRDS(object=posterior_drug_fits,file=file.path(opt$log_dir,'posterior_drug_fits.RDS'))
saveRDS(object=posterior_drug_assignments,file=file.path(opt$log_dir,'posterior_drug_assignments.RDS'))
saveRDS(object=posterior_cell_assignments,file=file.path(opt$log_dir,'posterior_cell_assignments.RDS'))
saveRDS(object=intersection.fitted.list,file=file.path(opt$log_dir,'intersection.fitted.list.RDS'))
```

Format a big data frame with all relevant posterior information.
```{r}
posterior_cell_assignments <- readRDS(file=file.path(opt$log_dir,'posterior_cell_assignments.RDS'))
posterior_drug_assignments <- readRDS(file=file.path(opt$log_dir,'posterior_drug_assignments.RDS'))

posterior <- posterior_cell_assignments %>%
  select(drug, cell, experiment, drug_type, cell_type, posterior, likelihood, value) %>%
  rename(cell_type_posterior=posterior,
         cell_type_likelihood=likelihood,
         realized_value=value) %>%
  group_by(drug, cell) %>% 
  mutate(num_experiments = n_distinct(experiment)) %>%
  ungroup() %>%
  left_join(posterior_drug_assignments %>%
              select(drug, p_prior, drug_type, posterior,likelihood) %>%
              rename(drug_type_posterior=posterior,
                     drug_type_likelihood=likelihood), by=c('drug_type','drug')) %>%
  mutate(cell_type = ifelse(cell_type == 'sensitive' & drug_type == 'broad',
                            'resistant',cell_type)) %>% #filter(drug==dr) %>% View
  mutate(cell_type_posterior = ifelse((cell_type == 'resistant' & drug_type == 'targeted') | drug_type=='broad',
                                      1-cell_type_posterior,cell_type_posterior)) %>%
  mutate(drug_type_posterior = ifelse(drug_type == 'broad', 1-drug_type_posterior,drug_type_posterior)) %>%
  rename(posterior_probability_sensitive = cell_type_posterior,
         posterior_probability_targeted = drug_type_posterior)
saveRDS(object=posterior,file=file.path(opt$log_dir,'posterior.formatted.RDS'))
```

Posterior drug type density plot.
```{r}
p <- posterior_drug_types %>% 
  crossing(x = seq(.001, .999, .001)) %>%
  group_by(experiment) %>%
  mutate(posterior = number/sum(number)) %>%
  ungroup() %>%
    mutate(density = posterior * dbeta(x, alpha, beta)) %>%
    ggplot(aes(x, density, color = drug_type, group = drug_type)) +
    geom_line() +
    facet_wrap(~ experiment,ncol=1) + 
    theme_bw() + 
        theme(strip.text.x = element_text(size = 18),
          legend.position='bottom',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=18),
          legend.title=element_text(size=18),
          title=element_text(size=18)) +
    labs(colour="Drug Type",y='Density',x='AOC') + 
    scale_x_continuous(limits = c(0,1), breaks=c(0,.5,1)) + 
    ggtitle('Posterior Drug-Type Densities')
  ggsave(p, file=file.path(opt$log_dir,meas,paste('posterior_drug_types.pdf',sep='')),width = 12, height = 8, units = "in")
  saveRDS(p, file.path(opt$log_dir,meas,paste('posterior_drug_types.RDS',sep='')))
```

Compute pairwise posterior drug assignments agreement.
```{r}
pairwise_drug_agreements <- tibble()
for (comp in names(intersection.fitted.list)) {
  combos <- t(combn(sort(unique(intersection.fitted.list[[comp]]$experiment)),2))
  for (combo in 1:nrow(combos)) {
    pairwise_drug_agreements <- posterior_drug_assignments %>% 
      filter(experiment %in% combos[combo,]) %>%
      select(drug:measure,posterior, drug_type,experiment) %>% 
      unite(temp,drug,measure,experiment,sep='__') %>%
      gather(key=var,value=val,-temp) %>% 
      separate(temp,into=c('drug','measure','experiment'),sep='__') %>%
      unite(var,experiment,var) %>%
      spread(var,val) %>% 
      na.omit %>%
      mutate_at(vars(paste(combos[combo,1],'posterior',sep='_'),paste(combos[combo,2],'posterior',sep='_')),as.numeric) %>%
      mutate_(g1 = paste(combos[combo,1],'drug_type',sep='_'), g2 = paste(combos[combo,2],'drug_type',sep='_')) %>%
      mutate(Called=case_when(g1==g2 & g1 == 'broad'~'Broadly-active',
                                 g1==g2 & g1 == 'targeted'~'Targeted',
                                 TRUE ~ 'Disagree')) %>%
      mutate(agreement = case_when(Called!='Disagree' ~ eval(parse(text=paste(combos[combo,1],'posterior',sep='_')))*
               eval(parse(text=paste(combos[combo,2],'posterior',sep='_'))) + 
                (1-eval(parse(text=paste(combos[combo,1],'posterior',sep='_'))))*
                (1-eval(parse(text=paste(combos[combo,2],'posterior',sep='_')))),
               TRUE ~ (1-eval(parse(text=paste(combos[combo,1],'posterior',sep='_'))))*
               eval(parse(text=paste(combos[combo,2],'posterior',sep='_'))) + 
                eval(parse(text=paste(combos[combo,1],'posterior',sep='_')))*
                (1-eval(parse(text=paste(combos[combo,2],'posterior',sep='_')))))) %>%
      select(drug, measure,agreement, Called) %>% 
      mutate(Intersection = comp, Comparison=paste(combos[combo,1],combos[combo,2],sep='_')) %>%
      bind_rows(pairwise_drug_agreements)
  }
}
```

Pairwise posterior drug assignments plots.
```{r}
library(ggrepel)
for (comp in names(intersection.fitted.list)) {
  combos <- t(combn(sort(unique(intersection.fitted.list[[comp]]$experiment)),2))
  for (combo in 1:nrow(combos)) {
  p <- posterior_drug_assignments %>% 
    filter(experiment %in% combos[combo,]) %>%
    mutate(posterior = case_when(drug_type=='broad' ~ 1-posterior,
                                 drug_type=='targeted' ~ posterior)) %>%
    select(drug:measure,posterior, drug_type,experiment) %>% 
    unite(temp,drug,measure,experiment,sep='__') %>%
    gather(key=var,value=val,-temp) %>% 
    separate(temp,into=c('drug','measure','experiment'),sep='__') %>%
    unite(var,experiment,var) %>%
    spread(var,val) %>% 
    na.omit %>%
    mutate_at(vars(paste(combos[combo,1],'posterior',sep='_'),paste(combos[combo,2],'posterior',sep='_')),as.numeric) %>%
    mutate_(g1 = paste(combos[combo,1],'drug_type',sep='_'), g2 = paste(combos[combo,2],'drug_type',sep='_')) %>%
    mutate(Agreement=case_when(g1==g2 & g1 == 'broad'~'Broadly-active',
                               g1==g2 & g1 == 'targeted'~'Targeted',
                               TRUE~ 'Disagree')) %>%
    ggplot(aes_string(x=paste(combos[combo,1],'posterior',sep='_'),
                y=paste(combos[combo,2],'posterior',sep='_'), 
                color = 'Agreement', 
                label='drug')) +
      geom_point() +
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      theme(strip.text.x = element_text(size = 18),
            legend.position='bottom',
            axis.text=element_text(size=16),
            axis.title=element_text(size=18),
            legend.text=element_text(size=18),
            legend.title=element_text(size=0),
            title=element_text(size=18)) +
      labs(y=combos[combo,2],x=combos[combo,1]) + 
      scale_x_continuous(limits = c(0,1), breaks=c(0,.5,1)) + 
      scale_y_continuous(limits = c(0,1), breaks=c(0,.5,1)) + 
      ggtitle('Posterior Probability of Targeted')
  ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('posterior_drug_types_individual.pdf',sep='')),width = 12, height = 8, units = "in")
  saveRDS(p, file.path(opt$log_dir,meas,comp,paste('posterior_drug_types_individual.RDS',sep='')))
  }
}
```

Compute pairwise posterior cell agreement.
```{r}
pairwise_cell_agreements <- tibble()
for (comp in names(intersection.fitted.list)) {
  combos <- t(combn(sort(unique(intersection.fitted.list[[comp]]$experiment)),2))
  for (combo in 1:nrow(combos)) {
    pairwise_cell_agreements <- intersection.fitted.list[[comp]] %>%
      filter(experiment %in% combos[combo,]) %>% 
      #filter(drug=='TAE684') %>%
      select(drug,cell,experiment, measure, cell_type, value, drug_type, posterior) %>%
      mutate(posterior = case_when(posterior==1 ~ .99,posterior==0 ~ .01,TRUE ~ posterior)) %>%
      mutate(posterior = case_when(drug_type=='broad' ~ 1-posterior,
                                   drug_type=='targeted' & cell_type=='resistant' ~ 1-posterior,
                                   TRUE ~ posterior)) %>% 
      gather(variable, value, -(drug:measure)) %>% 
      unite(temp, experiment, variable) %>%
      distinct(drug, cell, temp, measure, value) %>%
      spread(temp,value) %>%
      mutate_at(vars(ends_with('_value')),funs(as.numeric)) %>%
      mutate_at(vars(ends_with('_posterior')),funs(as.numeric)) %>%
      group_by(drug, cell, measure) %>%
      mutate_(g1 = paste(combos[combo,1],'drug_type',sep='_'), g2 = paste(combos[combo,2],'drug_type',sep='_')) %>%
      mutate(Called=case_when(g1==g2 & g1 == 'broad'~'Broadly-active',
                                 g1==g2 & g1 == 'targeted'~'Targeted',
                                 TRUE ~ 'Disagree')) %>% 
      mutate(agreement = eval(parse(text=paste(combos[combo,1],'posterior',sep='_')))*
               eval(parse(text=paste(combos[combo,2],'posterior',sep='_'))) + 
                (1-eval(parse(text=paste(combos[combo,1],'posterior',sep='_'))))*
                (1-eval(parse(text=paste(combos[combo,2],'posterior',sep='_'))))) %>% 
      mutate(Intersection = comp, Comparison=paste(combos[combo,1],combos[combo,2],sep='_')) %>%
      select(cell,drug,measure,agreement,Called, Intersection, Comparison) %>%
      bind_rows(pairwise_cell_agreements) 
  }
}
```

2-way concordance plots between studies for only those drugs/cells in the intersection, colored by posterior agreement.
```{r}
for (comp in names(intersection.fitted.list)) {
  dir.create(file.path(opt$log_dir,meas,comp,'by_drug'),showWarnings = FALSE)
  combos <- t(combn(sort(unique(intersection.fitted.list[[comp]]$experiment)),2))
  for (combo in 1:nrow(combos)) {
    p <- intersection.fitted.list[[comp]] %>%
      filter(experiment %in% combos[combo,]) %>% 
      mutate(posterior = case_when(posterior==1 ~ .99,posterior==0 ~ .01,TRUE ~ posterior)) %>%
      mutate(posterior = case_when(drug_type=='broad' ~ 1-posterior,
                                   drug_type=='targeted' & cell_type=='resistant' ~ 1-posterior,
                                   TRUE ~ posterior)) %>%
      select(drug,cell,experiment, measure, cell_type, value, drug_type, posterior) %>%
      gather(variable, value, -(drug:measure)) %>% 
      unite(temp, experiment, variable) %>%
      distinct(drug, cell, temp, measure, value) %>%
      spread(temp,value) %>%
      mutate_at(vars(ends_with('_value')),funs(as.numeric)) %>%
      mutate_at(vars(ends_with('_posterior')),funs(as.numeric)) %>%
      group_by(drug, cell, measure) %>%
      mutate_(g1 = paste(combos[combo,1],'drug_type',sep='_'), g2 = paste(combos[combo,2],'drug_type',sep='_')) %>%
      mutate(Called=case_when(g1==g2 & g1 == 'broad'~'Broadly-active',
                                 g1==g2 & g1 == 'targeted'~'Targeted',
                                 TRUE ~ 'Disagree')) %>%
      mutate(agreement = eval(parse(text=paste(combos[combo,1],'posterior',sep='_')))*
               eval(parse(text=paste(combos[combo,2],'posterior',sep='_'))) + 
                (1-eval(parse(text=paste(combos[combo,1],'posterior',sep='_'))))*
                (1-eval(parse(text=paste(combos[combo,2],'posterior',sep='_'))))) %>%
      ggplot(aes_string(x=paste(combos[combo,1],'value',sep='_'),
                        y=paste(combos[combo,2],'value',sep='_'))) + 
      geom_point(aes(color=agreement),alpha=.5,size=4) + 
      scale_colour_gradient2(midpoint=.5,limits = c(0,1),mid='grey50') + 
      theme_bw() + 
      facet_wrap(vars(drug),ncol=3) + 
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      scale_x_continuous(breaks=c(0,.5,1),labels=c('0','0.5','1'),limits = c(0,1)) +
      scale_y_continuous(breaks=c(0,.5,1),labels=c('0','0.5','1'),limits = c(0,1))
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('2way_posterior_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.pdf',sep='')),
         width = 10, height = 18, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('2way_posterior_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    drugs <- unique(intersection.fitted.list[[comp]]$drug)
    for (dr in drugs) {
      dr_short <- gsub("[^[:alnum:]]","",dr)
      dr_nonums <- gsub('[0-9]+', '', dr_short)
      if (nchar(dr_nonums)==0) {dr_short <- paste('drug',dr_short,sep='')}
      p <- intersection.fitted.list[[comp]] %>%
      mutate(posterior = case_when(posterior==1 ~ .99,posterior==0 ~ .01,TRUE ~ posterior)) %>%
      mutate(posterior = case_when(drug_type=='broad' ~ 1-posterior,
                                   drug_type=='targeted' & cell_type=='resistant' ~ 1-posterior,
                                   TRUE ~ posterior)) %>%
      filter(experiment %in% combos[combo,],drug==dr) %>% 
      select(drug,cell,experiment, measure, cell_type, value, drug_type, posterior) %>%
      gather(variable, value, -(drug:measure)) %>% 
      unite(temp, experiment, variable) %>%
      distinct(drug, cell, temp, measure, value) %>%
      spread(temp,value) %>%
      mutate_at(vars(ends_with('_value')),funs(as.numeric)) %>%
      mutate_at(vars(ends_with('_posterior')),funs(as.numeric)) %>%
      group_by(drug, cell, measure) %>%
      mutate_(g1 = paste(combos[combo,1],'drug_type',sep='_'), g2 = paste(combos[combo,2],'drug_type',sep='_')) %>%
      mutate(Called=case_when(g1==g2 & g1 == 'broad'~'Broadly-active',
                                 g1==g2 & g1 == 'targeted'~'Targeted',
                                 TRUE ~ 'Disagree')) %>%
      mutate(agreement = case_when(Called!='Disagree' ~ eval(parse(text=paste(combos[combo,1],'posterior',sep='_')))*
               eval(parse(text=paste(combos[combo,2],'posterior',sep='_'))) + 
                (1-eval(parse(text=paste(combos[combo,1],'posterior',sep='_'))))*
                (1-eval(parse(text=paste(combos[combo,2],'posterior',sep='_')))),
               Called=='Disagree' & g1 == 'broad' ~
                 (1-eval(parse(text=paste(combos[combo,1],'posterior',sep='_'))))*
                eval(parse(text=paste(combos[combo,2],'posterior',sep='_'))) +
                eval(parse(text=paste(combos[combo,1],'posterior',sep='_')))*
                (1-eval(parse(text=paste(combos[combo,2],'posterior',sep='_')))),
               Called=='Disagree' & g2 == 'broad' ~
                 (1-eval(parse(text=paste(combos[combo,1],'posterior',sep='_'))))*
                eval(parse(text=paste(combos[combo,2],'posterior',sep='_'))) +
                 eval(parse(text=paste(combos[combo,1],'posterior',sep='_')))*
                (1-eval(parse(text=paste(combos[combo,2],'posterior',sep='_')))),
               TRUE ~ eval(parse(text=paste(combos[combo,1],'posterior',sep='_')))*
               eval(parse(text=paste(combos[combo,2],'posterior',sep='_'))) + 
                (1-eval(parse(text=paste(combos[combo,1],'posterior',sep='_'))))*
                (1-eval(parse(text=paste(combos[combo,2],'posterior',sep='_')))))) %>%
      ggplot(aes_string(x=paste(combos[combo,1],'value',sep='_'),
                        y=paste(combos[combo,2],'value',sep='_'))) + 
      geom_point(aes(color=agreement),alpha=.5,size=4) + 
      scale_colour_gradient2(midpoint=.5,limits = c(0,1),mid='grey50',breaks=c(0,0.5,1),labels=c(0,0.5,1)) + 
      theme_bw() + 
      ggtitle(paste(dr,'Posterior Agreement')) +
      theme(strip.text.x = element_text(size = 12),
          legend.position='top',
          axis.text=element_text(size=12),
          axis.title=element_text(size=12),
          legend.text=element_text(size=12),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x=combos[combo,1],y=combos[combo,2]) + 
      scale_x_continuous(breaks=c(0,.5,1),labels=c('0','0.5','1'),limits = c(0,1)) +
      scale_y_continuous(breaks=c(0,.5,1),labels=c('0','0.5','1'),limits = c(0,1))
    ggsave(p,file=file.path(opt$log_dir,meas,comp,'by_drug',paste(dr_short,'_posterior_',
                                            combos[combo,1],'_',combos[combo,2],
                                            '.pdf',sep='')),
           width = 12, height = 8, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,'by_drug',paste(dr_short,'_posterior_',
                                            combos[combo,1],'_',combos[combo,2],
                                            '.RDS',sep='')))
    p <- intersection.fitted.list[[comp]] %>%
      mutate(posterior = case_when(posterior==1 ~ .99,posterior==0 ~ .01,TRUE ~ posterior)) %>%
      mutate(posterior = case_when(drug_type=='broad' ~ 1-posterior,
                                   drug_type=='targeted' & cell_type=='resistant' ~ 1-posterior,
                                   TRUE ~ posterior)) %>%
      filter(experiment %in% combos[combo,],drug==dr) %>% 
      select(drug,cell,experiment, measure, cell_type, value, drug_type, posterior) %>%
      gather(variable, value, -(drug:measure)) %>% 
      unite(temp, experiment, variable) %>%
      distinct(drug, cell, temp, measure, value) %>%
      spread(temp,value) %>%
      mutate_at(vars(ends_with('_value')),funs(as.numeric)) %>%
      mutate_at(vars(ends_with('_posterior')),funs(as.numeric)) %>%
      group_by(drug, cell, measure) %>%
      mutate_(g1 = paste(combos[combo,1],'drug_type',sep='_'), g2 = paste(combos[combo,2],'drug_type',sep='_')) %>%
      mutate(Called=case_when(g1==g2 & g1 == 'broad'~'Broadly-active',
                                 g1==g2 & g1 == 'targeted'~'Targeted',
                                 TRUE ~ 'Disagree')) %>%
      mutate(agreement = case_when(Called!='Disagree' ~ eval(parse(text=paste(combos[combo,1],'posterior',sep='_')))*
               eval(parse(text=paste(combos[combo,2],'posterior',sep='_'))) + 
                (1-eval(parse(text=paste(combos[combo,1],'posterior',sep='_'))))*
                (1-eval(parse(text=paste(combos[combo,2],'posterior',sep='_')))),
               Called=='Disagree' & g1 == 'broad' ~
                 (1-eval(parse(text=paste(combos[combo,1],'posterior',sep='_'))))*
                eval(parse(text=paste(combos[combo,2],'posterior',sep='_'))) +
                eval(parse(text=paste(combos[combo,1],'posterior',sep='_')))*
                (1-eval(parse(text=paste(combos[combo,2],'posterior',sep='_')))),
               Called=='Disagree' & g2 == 'broad' ~
                 (1-eval(parse(text=paste(combos[combo,1],'posterior',sep='_'))))*
                eval(parse(text=paste(combos[combo,2],'posterior',sep='_'))) +
                 eval(parse(text=paste(combos[combo,1],'posterior',sep='_')))*
                (1-eval(parse(text=paste(combos[combo,2],'posterior',sep='_')))),
               TRUE ~ eval(parse(text=paste(combos[combo,1],'posterior',sep='_')))*
               eval(parse(text=paste(combos[combo,2],'posterior',sep='_'))) + 
                (1-eval(parse(text=paste(combos[combo,1],'posterior',sep='_'))))*
                (1-eval(parse(text=paste(combos[combo,2],'posterior',sep='_')))))) %>%
      ggplot(aes_string(x=paste(combos[combo,1],'posterior',sep='_'),
                        y=paste(combos[combo,2],'posterior',sep='_'))) + 
      geom_point(aes(color=agreement),alpha=.5,size=4) + 
      scale_colour_gradient2(midpoint=.5,limits = c(0,1),mid='grey50',breaks=c(0,0.5,1),labels=c(0,0.5,1)) + 
      theme_bw() + 
      ggtitle(paste(dr,'Posterior probability sensitive')) +
      theme(strip.text.x = element_text(size = 12),
          legend.position='top',
          axis.text=element_text(size=12),
          axis.title=element_text(size=12),
          legend.text=element_text(size=12),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x=combos[combo,1],y=combos[combo,2]) + 
      scale_x_continuous(breaks=c(0,.5,1),labels=c('0','0.5','1'),limits = c(0,1)) +
      scale_y_continuous(breaks=c(0,.5,1),labels=c('0','0.5','1'),limits = c(0,1))
    ggsave(p,file=file.path(opt$log_dir,meas,comp,'by_drug',paste(dr_short,'_posterior_probsens_',
                                            combos[combo,1],'_',combos[combo,2],
                                            '.pdf',sep='')),
           width = 12, height = 8, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,'by_drug',paste(dr_short,'_posterior_probsens_',
                                            combos[combo,1],'_',combos[combo,2],
                                            '.RDS',sep='')))
    }
  }
}
```

Compute study agreements.
```{r}
pairwise_study_agreements <- tibble()
for (comp in names(intersection.fitted.list)) {
  combos <- t(combn(sort(unique(intersection.fitted.list[[comp]]$experiment)),2))
  for (combo in 1:nrow(combos)) {
   tdat <- intersection.fitted.list[[comp]] %>%
      filter(experiment %in% combos[combo,]) %>% 
      select(drug,cell,experiment, measure, cell_type, value, drug_type, posterior) %>%
      mutate(posterior = case_when(drug_type=='broad' ~ 1-posterior,
                                   drug_type=='targeted' & cell_type=='resistant' ~ 1-posterior,
                                   TRUE ~ posterior)) %>%
      gather(variable, value, -(drug:measure)) %>% 
      unite(temp, experiment, variable) %>%
      distinct(drug, cell, temp, measure, value) %>%
      spread(temp,value) %>%
      mutate_at(vars(ends_with('_value')),funs(as.numeric)) %>%
      mutate_at(vars(ends_with('_posterior')),funs(as.numeric)) 
   corrdat <- tdat %>%
      na.omit() %>%
      group_by(drug, measure) %>%
      summarise(pearson_corr = cor(eval(parse(text=paste(combos[combo,1],'value',sep='_'))),
                                eval(parse(text=paste(combos[combo,2],'value',sep='_'))),
                                method='pearson'),
             spearman_corr = cor(eval(parse(text=paste(combos[combo,1],'posterior',sep='_'))),
                                eval(parse(text=paste(combos[combo,2],'posterior',sep='_'))),
                                method='spearman')) %>%
      ungroup()
   lordat <- tdat %>% 
       group_by(drug, measure) %>% 
       na.omit() %>%
       mutate(Drug_type = case_when((eval(parse(text=paste(combos[combo,1],'drug_type',sep='_')))=='broad') & 
                                 (eval(parse(text=paste(combos[combo,2],'drug_type',sep='_')))=='broad') ~ 'Broad',
                                 (eval(parse(text=paste(combos[combo,1],'drug_type',sep='_')))=='targeted') & 
                                 (eval(parse(text=paste(combos[combo,2],'drug_type',sep='_')))=='targeted') ~ 'Targeted',
                                 TRUE ~ 'Disagree')) %>%
       summarise(Drug_type = first(Drug_type),
                 t00 = sum((eval(parse(text=paste(combos[combo,1],'cell_type',sep='_')))=='resistant') &
                           (eval(parse(text=paste(combos[combo,2],'cell_type',sep='_')))=='resistant')),
                 t11 = sum((eval(parse(text=paste(combos[combo,1],'cell_type',sep='_')))=='sensitive') &
                           (eval(parse(text=paste(combos[combo,2],'cell_type',sep='_')))=='sensitive')),
                 t01 = sum((eval(parse(text=paste(combos[combo,1],'cell_type',sep='_')))=='resistant') &
                           (eval(parse(text=paste(combos[combo,2],'cell_type',sep='_')))=='sensitive')),
                 t10 = sum((eval(parse(text=paste(combos[combo,1],'cell_type',sep='_')))=='sensitive') &
                           (eval(parse(text=paste(combos[combo,2],'cell_type',sep='_')))=='resistant'))) %>%
       mutate(t00 = t00+.5,
              t11 = t11+.5,
              t10 = t10+.5,
              t01 = t01+.5) %>% 
       ungroup() %>%
       mutate(LOR = log((t00*t11)/(t01*t10)),
              SE_LOR = sqrt(((1/t00)+(1/t11)+(1/t01) + (1/t10))),
              MCC = (t00*t11-t01*t10)/sqrt((t11+t01)*(t11+t10)*(t00+t10)*(t00+t01)))
     measuredat <- corrdat %>% 
       left_join(lordat, by=c('drug','measure'))
     pairwise_study_agreements <- measuredat %>% 
       mutate(Intersection = comp, Comparison=paste(combos[combo,1],combos[combo,2],sep='_')) %>% 
       bind_rows(pairwise_study_agreements)
  }
}
```

Calculate probability agree under varying thresholds and calculate AUC. Plot these.
```{r}
auc_prob <- tibble()
for (thresh in seq(0,1,by=.01)) {
  tdat <- pairwise_cell_agreements %>%
    group_by(drug, measure, Called, Intersection, Comparison) %>%
    summarise(Probability_agree = sum(agreement>=thresh)/n()) %>% 
    ungroup() %>%
    mutate(threshold=thresh)
  auc_prob <- auc_prob %>% bind_rows(tdat)
}
p50_prob <- auc_prob %>% 
  filter(threshold==.5)

auc_prob %>% 
  filter(threshold==.9, Called=='Targeted') %>%
  ggplot(aes(x=reorder(drug,Probability_agree),y=Probability_agree,fill=Called),color='black') + 
  geom_bar(stat = "identity", width = 0.5) +
  theme_bw() + 
  scale_fill_brewer(palette='Dark2') +
  coord_flip() + 
  theme(legend.position = 'none') +
  labs(fill='', title='Posterior probability of cell agreement',subtitle='Posteriors computed on full CCLE and GDSC datasets') +
  ylab('Probability(Agreement)') +
  xlab('Drug')
  

auc_prob <- auc_prob %>%
  group_by(drug) %>%
  do(auc = pracma::trapz(x=.$threshold,y=.$Probability_agree)) %>%
  mutate(auc = abs(unlist(auc))) %>%
  right_join(auc_prob, by='drug')

pairwise_study_agreements <- pairwise_study_agreements %>%
  left_join(auc_prob %>% distinct(drug, auc), by='drug') %>%
  left_join(p50_prob %>% distinct(drug, Probability_agree), by='drug')

pairwise_study_agreements %>%
  mutate(auc = case_when(Drug_type != 'Targeted' ~ pearson_corr,
                         TRUE ~ auc)) %>%
  ggplot(aes(x=reorder(drug,auc),y=pearson_corr,color=Drug_type, fill=Comparison)) + 
  geom_bar(stat = "identity", width = 0.5) +
  theme_bw() + 
  scale_fill_brewer(palette='Blues') +
  coord_flip() + 
  theme(legend.position = 'none') +
  labs(fill='', title='Pearson correlation',subtitle='Only intersected CCLE and GDSC datasets considered') +
  ylab('Correlation') +
  xlab('Drug') +
  ylim(0,1) +
  scale_color_manual(values=c(Targeted='blue',Disagree='red',Broad='red')) 

p <- auc_prob %>%
  filter(Called=='Targeted') %>%
  ggplot(aes(x=threshold,y=Probability_agree,color=Comparison)) +
  geom_line() +
  facet_wrap(vars(drug),ncol=5) + 
  theme_bw() + 
  theme(legend.position='top') +
  geom_abline(aes(slope=-1, intercept = 1), lwd = 1, lty=2) 
ggsave(p, file=file.path(opt$log_dir,meas,paste('auc_drug_level.png',sep='')),width = 12, height = 12, units = "in")
saveRDS(p, file=file.path(opt$log_dir,meas,paste('auc_drug_level.RDS',sep='')))

p <- auc_prob %>% 
  filter(threshold==.5) %>% 
  ggplot(aes(x=Probability_agree, y=auc, label=drug, color=Called)) + 
  geom_point() +
  geom_text_repel() + 
  theme(legend.position='top') +
  theme_bw()
ggsave(p, file=file.path(opt$log_dir,meas,paste('auc_prob50.pdf',sep='')),width = 8, height = 8, units = "in")
saveRDS(p, file=file.path(opt$log_dir,meas,paste('auc_prob50.RDS',sep='')))
```

Save cell, drug, and study agreements.
```{r}
saveRDS(object=pairwise_cell_agreements,file=file.path(opt$log_dir,'pairwise_cell_agreements.RDS'))
saveRDS(object=pairwise_drug_agreements,file=file.path(opt$log_dir,'pairwise_drug_agreements.RDS'))
saveRDS(object=pairwise_study_agreements,file=file.path(opt$log_dir,'pairwise_study_agreements.RDS'))
```

Plot pairwise correlations between sensitivity measures across drugs.
```{r}
for (comp in names(intersection.fitted.list)) {
  combos <- t(combn(sort(unique(intersection.fitted.list[[comp]]$experiment)),2))
  for (combo in 1:nrow(combos)) {
   tdat <- intersection.fitted.list[[comp]] %>%
      filter(experiment %in% combos[combo,]) %>% 
      select(drug,cell,experiment, measure, cell_type, value, drug_type, posterior) %>%
      mutate(posterior = case_when(drug_type=='broad' ~ 1-posterior,
                                   drug_type=='targeted' & cell_type=='resistant' ~ 1-posterior,
                                   TRUE ~ posterior)) %>%
      gather(variable, value, -(drug:measure)) %>% 
      unite(temp, experiment, variable) %>%
      distinct(drug, cell, temp, measure, value) %>%
      spread(temp,value) %>%
      mutate_at(vars(ends_with('_value')),list(as.numeric)) %>%
      mutate_at(vars(ends_with('_posterior')),list(as.numeric)) 
   corrdat <- tdat %>%
      group_by(drug, measure) %>% 
      summarise(pearson_corr = cor(eval(parse(text=paste(combos[combo,1],'value',sep='_'))),
                                eval(parse(text=paste(combos[combo,2],'value',sep='_'))),
                                method='pearson'),
             spearman_corr = cor(eval(parse(text=paste(combos[combo,1],'value',sep='_'))),
                                eval(parse(text=paste(combos[combo,2],'value',sep='_'))),
                                method='spearman'),
             pearson_corr_posterior = cor(eval(parse(text=paste(combos[combo,1],'posterior',sep='_'))),
                                eval(parse(text=paste(combos[combo,2],'posterior',sep='_'))),
                                method='pearson'),
             spearman_corr_posterior = cor(eval(parse(text=paste(combos[combo,1],'posterior',sep='_'))),
                                eval(parse(text=paste(combos[combo,2],'posterior',sep='_'))),
                                method='spearman')) %>%
      ungroup()
     lordat <- tdat %>% 
       group_by(drug, measure) %>% 
       mutate(Drug_type = case_when((eval(parse(text=paste(combos[combo,1],'drug_type',sep='_')))=='broad') & 
                                 (eval(parse(text=paste(combos[combo,2],'drug_type',sep='_')))=='broad') ~ 'Broad',
                                 (eval(parse(text=paste(combos[combo,1],'drug_type',sep='_')))=='targeted') & 
                                 (eval(parse(text=paste(combos[combo,2],'drug_type',sep='_')))=='targeted') ~ 'Targeted',
                                 TRUE ~ 'Disagree')) %>%
       summarise(Drug_type = first(Drug_type),
                 t00 = sum((eval(parse(text=paste(combos[combo,1],'cell_type',sep='_')))=='resistant') &
                           (eval(parse(text=paste(combos[combo,2],'cell_type',sep='_')))=='resistant')),
                 t11 = sum((eval(parse(text=paste(combos[combo,1],'cell_type',sep='_')))=='sensitive') &
                           (eval(parse(text=paste(combos[combo,2],'cell_type',sep='_')))=='sensitive')),
                 t01 = sum((eval(parse(text=paste(combos[combo,1],'cell_type',sep='_')))=='resistant') &
                           (eval(parse(text=paste(combos[combo,2],'cell_type',sep='_')))=='sensitive')),
                 t10 = sum((eval(parse(text=paste(combos[combo,1],'cell_type',sep='_')))=='sensitive') &
                           (eval(parse(text=paste(combos[combo,2],'cell_type',sep='_')))=='resistant'))) %>%
       mutate(t00 = t00+.5,
              t11 = t11+.5,
              t10 = t10+.5,
              t01 = t01+.5) %>% 
       ungroup() %>%
       mutate(LOR = log((t00*t11)/(t01*t10)),
              SE_LOR = sqrt(((1/t00)+(1/t11)+(1/t01) + (1/t10))),
              MCC = (t00*t11-t01*t10)/sqrt((t11+t01)*(t11+t10)*(t00+t10)*(t00+t01)))
     lordat_naive <- tdat %>% 
       group_by(drug, measure) %>% 
       mutate(Drug_type_naive = case_when(drug %in% c('17-AAG','paclitaxel','PD-0325901','AZD6244') ~ 'Broad',
                                    TRUE ~ 'Targeted')) %>%
       summarise(Drug_type_naive = first(Drug_type_naive),
                 t00 = sum(((eval(parse(text=paste(combos[combo,1],'value',sep='_')))<=.2 & Drug_type_naive=='Targeted') &
                           (eval(parse(text=paste(combos[combo,2],'value',sep='_')))<=.2)) | 
                           ((eval(parse(text=paste(combos[combo,1],'value',sep='_')))<=.4 & Drug_type_naive=='Broad') &
                           (eval(parse(text=paste(combos[combo,2],'value',sep='_')))<=.4))),
                 t11 = sum(((eval(parse(text=paste(combos[combo,1],'value',sep='_')))>.2 & Drug_type_naive=='Targeted') &
                           (eval(parse(text=paste(combos[combo,2],'value',sep='_')))>.2)) | 
                           ((eval(parse(text=paste(combos[combo,1],'value',sep='_')))>.4 & Drug_type_naive=='Broad') &
                           (eval(parse(text=paste(combos[combo,2],'value',sep='_')))>.4))),
                 t01 = sum(((eval(parse(text=paste(combos[combo,1],'value',sep='_')))<=.2 & Drug_type_naive=='Targeted') &
                           (eval(parse(text=paste(combos[combo,2],'value',sep='_')))>.2)) | 
                           ((eval(parse(text=paste(combos[combo,1],'value',sep='_')))<=.4 & Drug_type_naive=='Broad') &
                           (eval(parse(text=paste(combos[combo,2],'value',sep='_')))>.4))),
                 t10 = sum(((eval(parse(text=paste(combos[combo,1],'value',sep='_')))>.2 & Drug_type_naive=='Targeted') &
                           (eval(parse(text=paste(combos[combo,2],'value',sep='_')))<=.2)) | 
                           ((eval(parse(text=paste(combos[combo,1],'value',sep='_')))>.4 & Drug_type_naive=='Broad') &
                           (eval(parse(text=paste(combos[combo,2],'value',sep='_')))<=.4)))) %>%
       mutate(t00 = t00+.5,
              t11 = t11+.5,
              t10 = t10+.5,
              t01 = t01+.5) %>% 
       ungroup() %>%
       mutate(LOR_naive = log((t00*t11)/(t01*t10)),
              SE_LOR_naive = sqrt(((1/t00)+(1/t11)+(1/t01) + (1/t10))),
              MCC_naive = (t00*t11-t01*t10)/sqrt((t11+t01)*(t11+t10)*(t00+t10)*(t00+t01))) %>% 
       select(-t00,-t11,-t10,-t01)
     measuredat <- corrdat %>% 
       left_join(lordat, by=c('drug','measure')) %>%
       left_join(auc_prob %>% filter(Comparison==paste(combos[combo,1],combos[combo,2],sep='_'),
                                     Intersection == comp) %>%
                   distinct(drug,measure,auc),
                 by=c('drug','measure'))
     measuredat_naive <- corrdat %>% 
       left_join(lordat_naive, by=c('drug','measure')) %>%
       left_join(auc_prob %>% filter(Comparison==paste(combos[combo,1],combos[combo,2],sep='_'),
                                     Intersection == comp) %>%
                   distinct(drug,measure,auc),
                 by=c('drug','measure'))
     lordat_naive <- lordat %>% 
       select(-t00,-t11,-t10,-t01) %>%
       left_join(lordat_naive, by=c('drug','measure'))  %>%
       left_join(auc_prob %>% filter(Comparison==paste(combos[combo,1],combos[combo,2],sep='_'),
                                     Intersection == comp) %>%
                   distinct(drug,measure,auc),
                 by=c('drug','measure'))
     
    # spearman vs pearson, original sensitivity measure
    p <-  measuredat_naive %>% 
       mutate(mycolor = case_when(drug %in% c('17-AAG','paclitaxel','PD-0325901') ~ 'red',
                                  TRUE ~ 'black')) %>%
      ggplot(aes(x=spearman_corr,y=pearson_corr,label=drug)) + 
      geom_point(aes(color=mycolor), show.legend=FALSE,alpha=.8,size=4) + 
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      geom_abline(aes(slope=1,intercept=0),lty=2) +
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=24)) +
      scale_color_manual(values=c(red='red',black='black')) +
      xlim(c(-.1,1)) + ylim(c(-.1,1)) +
      labs(x='Spearman',y='Pearson', title='Continuous measures of agreement',subtitle='Associations for commonly-assayed cells and drugs') 
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Spearman_Pearson_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.png',sep='')),
         width = 12, height = 12, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('Spearman_Pearson_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # spearman vs pearson, posterior sensitivity measure
    p <- ggplot(measuredat %>% mutate(Drug_type_naive = case_when(drug %in% c('17-AAG','paclitaxel','PD-0325901') ~ 'Broad effect',
                                    TRUE ~ 'Narrow effect')), aes(x=spearman_corr_posterior,y=pearson_corr_posterior,label=drug)) + 
      geom_point(aes(color=Drug_type),alpha=.8,size=4,show.legend=FALSE) + 
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      geom_abline(aes(slope=1,intercept=0),lty=2) +
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x='Model-based Spearman',y='Model-based Pearson') +
      xlim(c(-.1,1)) + ylim(c(-.1,1))
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Spearman_Pearson_posterior_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.pdf',sep='')),
         width = 5, height = 5, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('Spearman_Pearson_posterior_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # spearman vs posterior
    p <- ggplot(measuredat%>% mutate(Drug_type_naive = case_when(drug %in% c('17-AAG','paclitaxel','PD-0325901') ~ 'Broad effect',
                                    TRUE ~ 'Narrow effect')), aes(x=spearman_corr,y=spearman_corr_posterior,label=drug)) + 
      geom_point(aes(color=Drug_type_naive),alpha=.8,size=4,show.legend=FALSE) + 
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      geom_abline(aes(slope=1,intercept=0),lty=2) +
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x='Spearman',y='Model-based Spearman') +
      xlim(c(-.1,1)) + ylim(c(-.1,1))
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Spearman_Spearman_posterior_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.pdf',sep='')),
         width = 5, height = 5, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('Spearman_Spearman_posterior_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # pearson vs posterior
    p <- ggplot(measuredat%>% mutate(Drug_type_naive = case_when(drug %in% c('17-AAG','paclitaxel','PD-0325901') ~ 'Broad effect',
                                    TRUE ~ 'Narrow effect')), aes(x=pearson_corr,y=pearson_corr_posterior,label=drug)) + 
      geom_point(aes(color=Drug_type_naive),alpha=.8,size=4,show.legend=FALSE) + 
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      geom_abline(aes(slope=1,intercept=0),lty=2) +
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x='Pearson',y='Model-based Pearson') +
      xlim(c(-.1,1)) + ylim(c(-.1,1))
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Pearson_Pearson_posterior_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.pdf',sep='')),
         width = 5, height = 5, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('Pearson_Pearson_posterior_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # log-odds naive v log-odds
    p <- ggplot(lordat_naive, aes(x=LOR_naive,y=LOR,label=drug)) + 
      geom_point(aes(color=Drug_type_naive),show.legend=FALSE,alpha=.8,size=4) +
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      geom_abline(aes(slope=1,intercept=0),lty=2) +
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x='Log-odds ratio',y='Model-based log-odds ratio') +
      xlim(c(0,10)) + ylim(c(0,10))
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Naive_LOR_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.pdf',sep='')),
         width = 5, height = 5, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('Naive_LOR_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # log-odds naive v MCC naive
    p <- ggplot(lordat_naive, aes(x=LOR_naive,y=MCC_naive,label=drug)) + 
      geom_point(aes(color=Drug_type_naive),show.legend=FALSE,alpha=.8,size=4) +
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x='Log-odds ratio',y='MCC') +
      xlim(c(0,10)) + ylim(c(0,1))
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Naive_LOR_MCC_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.pdf',sep='')),
         width = 5, height = 5, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('Naive_LOR_MCC_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # spearman naive v MCC naive
    p <- ggplot(measuredat_naive %>% 
       mutate(mycolor = case_when(drug %in% c('Nilotinib','PLX4720','Crizotinib') ~ 'purple',
                                  drug %in% c('PD-0325901','17-AAG') ~ 'green',
                                  drug %in% c('PHA-665752','Nutlin-3') ~ 'red',
                                  TRUE ~ 'blue')), aes(x=spearman_corr,y=MCC_naive,label=drug)) + 
      geom_point(aes(color=mycolor),show.legend=FALSE,alpha=.8,size=4) +
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=24)) +
      labs(x='Spearman Correlation',y='Matthews Correlation', title='Alternate measures of agreement',subtitle='Associations for commonly-assayed cells and drugs') +
      xlim(c(0-.1,1)) + ylim(c(0,1)) + 
      scale_color_manual(values=c(purple='purple',green='green',red='red',blue='blue')) 
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Naive_Spearman_Naive_MCC_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.png',sep='')),
         width = 12, height = 12, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('Naive_Spearman_Naive_MCC_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # pearson naive v MCC naive
    p <- ggplot(measuredat_naive %>% 
       mutate(mycolor = case_when(drug %in% c('Nilotinib','PLX4720','Crizotinib-0325901') ~ 'purple',
                                  drug %in% c('PD-0325901','17-AAG') ~ 'green',
                                  drug %in% c('PHA-66752','Nutlin-3') ~ 'red',
                                  TRUE ~ 'blue')), aes(x=pearson_corr,y=MCC_naive,label=drug)) + 
      geom_point(aes(color=mycolor),show.legend=FALSE,alpha=.8,size=4) +
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=24)) +
      labs(x='Pearson Correlation',y='Matthews Correlation', title='Continuous measures of agreement',subtitle='Associations for commonly-assayed cells and drugs') +
      xlim(c(0,1)) + ylim(c(0,1)) + 
      scale_color_manual(values=c(purple='purple',green='green',red='red',blue='blue')) 
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Naive_Pearson_Naive_MCC_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.png',sep='')),
         width = 12, height = 12, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('Naive_Pearson_Naive_MCC_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # LO naive v MCC naive
    p <- ggplot(measuredat_naive %>% 
       mutate(mycolor = case_when(drug %in% c('Nilotinib','PLX4720','Crizotinib') ~ 'purple',
                                  drug %in% c('PD-0325901','17-AAG') ~ 'green',
                                  drug %in% c('PHA-665752','Nutlin-3') ~ 'red',
                                  TRUE ~ 'blue')), aes(x=LOR_naive,y=MCC_naive,label=drug)) + 
      geom_point(aes(color=mycolor),show.legend=FALSE,alpha=.8,size=4) +
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=24)) +
      labs(x='Log-Odds',y='Matthews Correlation', title='Binary measures of agreement',subtitle='Associations for commonly-assayed cells and drugs') +
      ylim(c(0,1)) + 
      scale_color_manual(values=c(purple='purple',green='green',red='red',blue='blue')) 
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Naive_LO_Naive_MCC_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.png',sep='')),
         width = 12, height = 12, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('Naive_LO_Naive_MCC_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # MCC naive v MCC
    p <- ggplot(lordat_naive%>% mutate(Drug_type_naive = case_when(drug %in% c('17-AAG','paclitaxel','PD-0325901',
                                                                             'TAE684','AZD6244','PD-0332991') ~ 'Broad effect')),
                                                                 aes(x=MCC_naive,y=MCC,label=drug)) + 
      geom_point(aes(color=Drug_type_naive),show.legend=FALSE,alpha=.8,size=4) +
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      geom_abline(aes(slope=1,intercept=0),lty=2) +
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x='MCC',y='Model-based MCC') +
      xlim(c(0,1)) + ylim(c(0,1))
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Naive_MCC_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.pdf',sep='')),
         width = 5, height = 5, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('Naive_MCC_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # posterior MCC v posterior LO
    p <- ggplot(lordat_naive, aes(x=LOR,y=MCC,label=drug)) + 
      geom_point(aes(color=Drug_type),show.legend=FALSE,alpha=.8,size=4) +
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x='Model-based Log-odds',y='Model-based MCC') +
      xlim(c(0,10)) + ylim(c(0,1))
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('LOR_MCC_model_fit',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.pdf',sep='')),
         width = 5, height = 5, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('LOR_MCC_model_fit',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # posterior MCC v posterior auc
    p <- ggplot(lordat_naive, aes(x=MCC,y=auc,label=drug)) + 
      geom_point(aes(color=Drug_type),show.legend=FALSE,alpha=.8,size=4) +
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x='Model-based MCC',y='Model-based AUC') +
      xlim(c(0,10))
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('MCC_AUC_model_fit',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.pdf',sep='')),
         width = 5, height = 5, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('MCC_AUC_model_fit',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # posterior LO v posterior auc
    p <- ggplot(lordat_naive, aes(x=LOR,y=auc,label=drug)) + 
      geom_point(aes(color=Drug_type),show.legend=FALSE,alpha=.8,size=4) +
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x='Model-based Log-odds',y='Model-based AUC') +
      xlim(c(0,10)) 
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('LOR_AUC_model_fit',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.pdf',sep='')),
         width = 5, height = 5, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('LOR_AUC_model_fit',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # spearman v auc
    p <- ggplot(measuredat%>% mutate(Drug_type_naive = case_when(drug %in% c('17-AAG','paclitaxel','PD-0325901') ~ 'Broad effect',
                                    TRUE ~ 'Narrow effect')), aes(x=spearman_corr,y=auc,label=drug)) + 
      geom_point(aes(color=Drug_type_naive),show.legend=FALSE,alpha=.8,size=4) +
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x='Spearman',y='Model-based AUC') +
      xlim(c(-.1,1)) 
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Spearman_auc_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.pdf',sep='')),
         width = 8, height = 8, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('Spearman_auc_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # model based spearman v auc
    p <- ggplot(measuredat%>% mutate(Drug_type_naive = case_when(drug %in% c('17-AAG','paclitaxel','PD-0325901') ~ 'Broad effect',
                                    TRUE ~ 'Narrow effect')), aes(x=spearman_corr_posterior,y=auc,label=drug)) + 
      geom_point(aes(color=Drug_type),show.legend=FALSE,alpha=.8,size=4) +
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x='Model-based Spearman',y='Model-based AUC') +
      xlim(c(-.1,1)) 
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Spearman_posterior_auc_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.pdf',sep='')),
         width = 8, height = 8, units = "in")
    # model based pearson v auc
    p <- ggplot(measuredat%>% mutate(Drug_type_naive = case_when(drug %in% c('17-AAG','paclitaxel','PD-0325901') ~ 'Broad effect',
                                    TRUE ~ 'Narrow effect')), aes(x=pearson_corr_posterior,y=auc,label=drug)) + 
      geom_point(aes(color=Drug_type),show.legend=FALSE,alpha=.8,size=4) +
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x='Model-based Pearson',y='Model-based AUC') +
      xlim(c(-.1,1)) + ylim(c(0,10))
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Pearson_posterior_auc_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.pdf',sep='')),
         width = 8, height = 8, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('Spearman_auc_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # spearman v log-odds
    p <- ggplot(measuredat%>% mutate(Drug_type_naive = case_when(drug %in% c('17-AAG','paclitaxel','PD-0325901') ~ 'Broad effect',
                                    TRUE ~ 'Narrow effect')), aes(x=spearman_corr,y=LOR,label=drug)) + 
      geom_point(aes(color=Drug_type_naive),show.legend=FALSE,alpha=.8,size=4) +
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x='Spearman',y='Model-based log-odds ratio') +
      xlim(c(-.1,1)) + ylim(c(0,10))
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Spearman_LOR_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.pdf',sep='')),
         width = 8, height = 8, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('Spearman_LOR_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # spearman v naive log-odds
    p <- ggplot(measuredat_naive, aes(x=spearman_corr,y=LOR_naive,label=drug)) + 
      geom_point(aes(color=Drug_type_naive),show.legend=FALSE,alpha=1,size=2) +
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x='Spearman',y='Log-odds ratio') +
      xlim(c(-.1,1)) + ylim(c(0,10))
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Spearman_LOR_naive_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.pdf',sep='')),
         width = 5, height = 5, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('Spearman_LOR_naive_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # pearson v auc
    p <- ggplot(measuredat%>% mutate(Drug_type_naive = case_when(drug %in% c('17-AAG','paclitaxel','PD-0325901',
                                                                             'TAE684','AZD6244','PD-0332991') ~ 'Broad effect',
                                    TRUE ~ 'Narrow effect')), aes(x=pearson_corr,y=auc,label=drug)) + 
      geom_point(aes(color=Drug_type_naive),alpha=.8,size=4,show.legend=FALSE) + 
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x='Pearson',y='Model-based AUC') +
      xlim(c(-.1,1)) + ylim(c(0,1))
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Pearson_auc_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.png',sep='')),
         width = 5, height = 5, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('Pearson_auc_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # pearson v log-odds
    p <- ggplot(measuredat%>% mutate(Drug_type_naive = case_when(drug %in% c('17-AAG','paclitaxel','PD-0325901') ~ 'Broad effect',
                                    TRUE ~ 'Narrow effect')), aes(x=pearson_corr,y=LOR,label=drug)) + 
      geom_point(aes(color=Drug_type_naive),alpha=.8,size=4,show.legend=FALSE) + 
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x='Pearson',y='Model-based log-odds ratio') +
      xlim(c(-.1,1)) + ylim(c(0,10))
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Pearson_LOR_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.pdf',sep='')),
         width = 5, height = 5, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('Pearson_LOR_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
    # pearson v naive log-odds
    p <- ggplot(measuredat_naive, aes(x=pearson_corr,y=LOR_naive,label=drug)) + 
      geom_point(aes(color=Drug_type_naive),alpha=.8,size=4,show.legend=FALSE) + 
      geom_text_repel(show.legend=FALSE,size=5) + 
      theme_bw() + 
      theme(strip.text.x = element_text(size = 18),
          legend.position='top',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=0),
          title=element_text(size=14)) +
      labs(x='Pearson',y='Log-odds ratio') +
      xlim(c(-.1,1)) + ylim(c(0,10))
    ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Pearson_LOR_naive_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.pdf',sep='')),
         width = 5, height = 5, units = "in")
    saveRDS(p,file.path(opt$log_dir,meas,comp,paste('Pearson_LOR_naive_',
                                          combos[combo,1],'_',combos[combo,2],
                                          '.RDS',sep='')))
  }
}
```

Plot agreements for all pairwise study comparisons.
```{r}
p <- pairwise_study_agreements %>% 
  mutate(Drug_type = ifelse(Drug_type == 'Targeted','AUC','Spearman')) %>%
  filter(Drug_type == 'AUC') %>%
  group_by(Comparison) %>%
  arrange(desc(auc)) %>%
  mutate(label = ifelse(row_number() %in% c(1:3,n()),drug,'')) %>%
  ungroup() %>%
  ggplot(aes(x=spearman_corr,y=auc,color=Comparison,label=label)) +
  geom_point(alpha=.5,size=1.5) +
  geom_text_repel(show.legend=FALSE,size=4) +
  theme_bw() 
ggsave(p, file=file.path(opt$log_dir,meas,paste('pairwise_study_agreements_targeted.pdf',sep='')),width = 8, height = 8, units = "in")
saveRDS(p, file=file.path(opt$log_dir,meas,paste('pairwise_study_agreements_targeted.RDS',sep='')))
p <- pairwise_study_agreements %>% 
  mutate(Drug_type = ifelse(Drug_type == 'Targeted','AUC','{Pearson')) %>%
  filter(Drug_type == 'Pearson') %>%
  group_by(Comparison) %>%
  arrange(desc(pearson_corr)) %>%
  mutate(label = ifelse(row_number() %in% c(1:3,n()),drug,'')) %>%
  ungroup() %>%
  ggplot(aes(x=spearman_corr,y=pearson_corr,color=Comparison,label=label)) +
  geom_point(alpha=.5,size=1.5) +
  geom_text_repel(show.legend=FALSE,size=4) +
  theme_bw() 
ggsave(p, file=file.path(opt$log_dir,meas,paste('pairwise_study_agreements_broad.pdf',sep='')),width = 8, height = 8, units = "in")
saveRDS(p, file=file.path(opt$log_dir,meas,paste('pairwise_study_agreements_broad.RDS',sep='')))
```

Plot density agreements for all pairwise cell comparisons.
```{r}
p <- pairwise_cell_agreements %>% 
  ungroup() %>%
  mutate(Drug_type = ifelse(Called == 'Targeted','Targeted','Broad')) %>%
  filter(Drug_type=='Targeted') %>%
  mutate(drug=as.factor(drug)) %>% 
  mutate(drug=reorder(drug, agreement, mean)) %>%
  ggplot(aes(x=agreement,y=drug, fill = Comparison),show.legend=FALSE) +
  geom_density_ridges(alpha = .2, show.legend=FALSE) +
  geom_point(shape="|", show.legend=FALSE) + 
  theme_bw() +  
  #facet_wrap(vars(Comparison),nrow=1,scales='free') +
  scale_fill_brewer(palette="Dark2") +
  theme(axis.title.y = element_blank(), axis.title.x = element_blank()) + 
  theme(strip.text.x = element_text(size = 20),
        legend.text=element_text(size=20),
        legend.title=element_text(size=20),
        legend.position="top",
        axis.text=element_text(size=20),
        axis.title = element_text(size=20),
        plot.title = element_text(size = 20))
ggsave(p, file=file.path(opt$log_dir,meas,paste('pairwise_cell_agreements_targeted.pdf',sep='')),width = 6, height = 8, units = "in")
saveRDS(p, file=file.path(opt$log_dir,meas,paste('pairwise_cell_agreements_targeted.RDS',sep='')))  
p <- pairwise_cell_agreements %>% 
  ungroup() %>%
  mutate(Drug_type = ifelse(Called == 'Targeted','Targeted','Broad')) %>%
  filter(Drug_type=='Broad') %>%
  mutate(drug=as.factor(drug)) %>% 
  mutate(drug=reorder(drug, agreement, mean)) %>%
  ggplot(aes(x=agreement,y=drug, fill = Comparison),show.legend=FALSE) +
  geom_density_ridges(alpha = .2, show.legend=FALSE) +
  geom_point(shape="|", show.legend=FALSE) + 
  theme_bw() +  
  #facet_wrap(vars(Comparison),nrow=1,scales='free') +
  scale_fill_brewer(palette="Dark2") +
  theme(axis.title.y = element_blank(), axis.title.x = element_blank()) + 
  theme(strip.text.x = element_text(size = 20),
        legend.text=element_text(size=20),
        legend.title=element_text(size=20),
        legend.position="top",
        axis.text=element_text(size=20),
        axis.title = element_text(size=20),
        plot.title = element_text(size = 20)) + 
  scale_x_continuous(limits=c(0,1))
ggsave(p, file=file.path(opt$log_dir,meas,paste('pairwise_cell_agreements_broad.pdf',sep='')),width = 6, height = 8, units = "in")
saveRDS(p, file=file.path(opt$log_dir,meas,paste('pairwise_cell_agreements_broad.RDS',sep='')))  
```

Final agreement barplot.
```{r}
p <- pairwise_study_agreements %>% 
  select(drug, measure, pearson_corr, Drug_type, auc, Intersection, Comparison) %>% 
  gather(measure, value, pearson_corr, auc) %>%
  filter((Drug_type!='Targeted' & measure=='pearson_corr') | (Drug_type=='Targeted' & measure=='auc')) %>%
  mutate(drug = reorder(drug, value)) %>%
  mutate(value = round(value,2)) %>%
  ggplot(aes(drug, value, label = value, fill=Comparison)) +   
  geom_bar(aes(color=Drug_type), stat = "identity", width = 0.5) +
  geom_text(nudge_y = 0.05,  size = 3) +
  theme_bw() + 
  scale_fill_brewer(palette='Blues') +
  scale_color_brewer(palette='Dark2', guide=FALSE) +
  coord_flip() + 
  theme(legend.position = 'top') +
  labs(fill='') +
  ylab('Agreement') +
  xlab('') 
ggsave(p, file=file.path(opt$log_dir,meas, paste('final_agreements.pdf',sep='')),width = 4, height = 8, units = "in")
saveRDS(p, file=file.path(opt$log_dir,meas,paste('final_agreements.RDS',sep='')))  

p <- pairwise_study_agreements %>% 
  select(drug, measure, auc, Drug_type, Intersection, Comparison) %>% 
  gather(measure, value, auc) %>%
  mutate(drug = reorder(drug, value)) %>%
  mutate(value = round(value,2)) %>%
  ggplot(aes(drug, value, label = value, fill=Comparison)) +   
  geom_bar(aes(color=Drug_type), stat = "identity", width = 0.5) +
  geom_text(nudge_y = 0.05,  size = 3) +
  theme_bw() + 
  scale_fill_brewer(palette='Blues') +
  scale_color_brewer(palette='Dark2', guide=FALSE) +
  coord_flip() + 
  theme(legend.position = 'top') +
  labs(fill='') +
  ylab('AUC') +
  xlab('') 
ggsave(p, file=file.path(opt$log_dir,meas, paste('final_auc_agreements.pdf',sep='')),width = 4, height = 8, units = "in")
saveRDS(p, file=file.path(opt$log_dir,meas,paste('final_auc_agreements.RDS',sep='')))  
```

For broadly-active drugs, calculate the difference between the posteriors. 
```{r, eval=FALSE}
new_pairwise_cell_agreements <- tibble()
for (comp in names(intersection.fitted.list)) {
  combos <- t(combn(sort(unique(intersection.fitted.list[[comp]]$experiment)),2))
  for (combo in 1:nrow(combos)) {
    new_pairwise_cell_agreements <- intersection.fitted.list[[comp]] %>%
      filter(experiment %in% combos[combo,]) %>% 
      select(drug,cell,experiment, measure, cell_type, value, drug_type, posterior) %>%
      mutate(posterior = case_when(posterior==1 ~ .99,posterior==0 ~ .01,TRUE ~ posterior)) %>%
      gather(variable, value, -(drug:measure)) %>% 
      unite(temp, experiment, variable) %>%
      distinct(drug, cell, temp, measure, value) %>%
      spread(temp,value) %>%
      mutate_at(vars(ends_with('_value')),funs(as.numeric)) %>%
      mutate_at(vars(ends_with('_posterior')),funs(as.numeric)) %>%
      group_by(drug, cell, measure) %>%
      mutate_(g1 = paste(combos[combo,1],'drug_type',sep='_'), g2 = paste(combos[combo,2],'drug_type',sep='_')) %>%
      mutate(Called=case_when(g1==g2 & g1 == 'broad'~'Broadly-active',
                                 g1==g2 & g1 == 'targeted'~'Targeted',
                                 TRUE ~ 'Disagree')) %>% 
      filter(Called=='Broadly-active') %>%
      mutate(Diff = eval(parse(text=paste(combos[combo,1],'posterior',sep='_'))) - eval(parse(text=paste(combos[combo,2],'posterior',sep='_')))) %>%
      group_by(drug, measure) %>%
      mutate(diff_mean = mean(Diff),
             diff_sd = sd(Diff)) %>%
      ungroup() %>%
      mutate(threshold_high = qnorm(.975, mean=diff_mean, sd=diff_sd)) %>%
      mutate(threshold_low = qnorm(.025, mean=diff_mean, sd=diff_sd)) %>%
      mutate(agree = case_when((Diff<=threshold_high) & (Diff>=threshold_low) ~ TRUE,
                               TRUE ~ FALSE)) %>%
      mutate(Intersection = comp, Comparison=paste(combos[combo,1],combos[combo,2],sep='_')) %>%
      select(cell,drug,measure,Called, Intersection, Comparison, agree) %>%
      bind_rows(new_pairwise_cell_agreements) 
  }
}
```

Hard threshold cell agreements as agree/disagree and calculate proportions per drug.
```{r, eval=FALSE}
pairwise_cell_agreements %>% 
  ungroup() %>%
  filter(Called == 'Targeted') %>%
  mutate(agree = agreement>=.975) %>%
  bind_rows(new_pairwise_cell_agreements) %>%
  group_by(drug, measure, Comparison, Intersection, Called) %>%
  summarise(prop_agree = mean(agree)) %>%
  ungroup()
```

Load known biomarkers (gene-drug associations).
```{r, eval=FALSE}
library(readxl)
gene_drug_asociations <- read_excel(opt$biomarkers_file, sheet = "mutation") %>%
  as_tibble() %>%
  bind_rows(read_excel(opt$biomarkers_file, sheet = "copy_number_variation"),
            read_excel(opt$biomarkers_file, sheet = "expression")) %>%
  mutate(type=case_when(type=='expression' ~ 'rna',
                        type=='copy_number_variation' ~ 'cnv',
                        TRUE ~ type))
```

Calculate biomarker effect sizes.
```{r,eval=FALSE}
library(PharmacoGx)
new_sProfiles_all <- posterior_cell_assignments
rez <- tibble()
for (dataset in opt$datasets) {
  #load(file.path('../PSets',paste(dataset,'RData',sep='.')))
  load(file.path('PSets',paste(dataset,'RData',sep='.')))
  eval(parse(text = paste('tempPset <- ',dataset,sep='')))
  for (feat in c('cnv','rna','mutation')) {
    features <- gene_drug_asociations %>%
      filter(type==feat) %>%
      distinct(gene) %>% 
      pull()
    drugs <- gene_drug_asociations %>%
      filter(type==feat) %>%
      distinct(compound) %>% 
      pull() 
    idx <- which(featureInfo(tempPset,feat)$Symbol %in% features)
    molfeatures <- fNames(tempPset, feat)[idx]
    genefeatures <- featureInfo(tempPset,feat)$Symbol[idx]
    if (!is.null(genefeatures)) {
      concor <- tibble(ID=molfeatures,gene=genefeatures)
    } else {
      concor <- tibble(ID=molfeatures,gene=NA)
    }
    sProfiles <- summarizeSensitivityProfiles(tempPset, sensitivity.measure = opt$sensitivity_measure, summary.stat = 'median', verbose = FALSE) %>%
      as.data.frame() %>%
      rownames_to_column('drug') %>%
      as_tibble() %>%
      gather(key='cell',value='value',-drug) %>%
      group_by(drug) %>%
      mutate(waterfall=PharmacoGx:::callingWaterfall(value,type='AUC')) %>%
      ungroup() %>% 
      rename(!!opt$sensitivity_measure := value)
    sig.rna <- lapply(c(opt$sensitivity_measure,'waterfall','cell_type'), function(jj) {
      new_sProfile <- new_sProfiles_all %>%
        filter(experiment==dataset) %>%
        select(drug,cell,cell_type) %>%
        mutate(cell_type = as.factor(cell_type)) %>%
        right_join(sProfiles, by=c('drug','cell')) %>%
        select(drug, cell, jj) %>% 
        spread(key='cell',value=jj) %>%
        as.data.frame() %>%
        column_to_rownames('drug')
      ss <- data.frame()
      for (molfeat in molfeatures) {
        tt <- try(drugSensitivitySig(pSet=tempPset,
                                  mDataType=feat,
                                  drugs=drugs,
                                  features=molfeat,
                                  molecular.summary.stat="median",
                                  sensitivity.summary.stat="median",
                                  verbose=TRUE,
                                  sProfiles=new_sProfile), silent = TRUE)
        if (!(class(tt) == 'try-error')) {
          ss <- bind_rows(ss,as.data.frame(tt) %>% 
                            mutate(ID=molfeat))
        }
      }
      if (nrow(ss) > 0) {
        ss %>%
          as_tibble() %>%
          mutate(method=jj) %>%
          gather(key='compound',value='value',-c('ID','method')) %>%
          separate(compound,into=c('compound','statistic'),sep="[.]") %>%
          left_join(concor, by='ID') %>%
          select(-ID) %>%
          mutate(dataset = dataset)
      } else {
        ss
      }
    })
    rez <- bind_rows(rez,do.call(rbind,sig.rna))
  }
}
saveRDS(object=rez,file=file.path(opt$log_dir,'biomarker_effect_sizes.RDS'))
saveRDS(object=gene_drug_asociations,file=file.path(opt$log_dir,'gene_drug_asociations.RDS'))
```

Clear environment.
```{r}
rm(list=ls(all.names = TRUE))
```

