---
title: "Estimate posterior concordance"
author: "Matt Ploenzke"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Estimate concordance}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Set up and load packages.
```{r setup, include=FALSE}
  rm(list=ls(all=TRUE))
  knitr::opts_chunk$set(echo = TRUE)
  library(PharmacoMixtuR)
  library(tidyverse)
  library(ggridges)
```

Set options.
```{r}
  opt <- list()
  opt$datasets <- c("CCLE", "GDSC1000", 'CTRPv2', 'FIMM','gCSI') # CCLE GDSC GDSC1000 gCSI FIMM CTRPv2
  #opt$datasets <- c("CCLE", "GDSC")
  #opt$biomarkers_file <- '~/Desktop/Concordance/PSets/gene_drug_asociations.xlsx'
  opt$biomarkers_file <- '~/concordance/PSets/gene_drug_asociations.xlsx'
  opt$min_intersection <- 1 # Minimum number of studies a drug/cell must be assayed in to be included in the intersection comparison
  opt$log_dir <- paste(paste(opt$datasets,collapse='_'),'fit_joint',sep='_')
  opt$sensitivity_measure <- c('auc_recomputed') # raw_auc e_inf hill_slope ec50 auc_recomputed
  opt$use_small_datasets <- FALSE
  # Prior specifications denoting cell sensitivity and proportion of drugs broadly-active:
  opt$prior.sensitive <- .6 #.3 # prior specification denoting cell is sensitive if greater than this value
  opt$prior.broadly.active <- 'median_mad' #median.05 # prior specification denoting drug is broadly-active if probability cell is sensitive is greater than value
  opt$run_on_cluster <- TRUE # this just changes file paths depending on where the code is being run
```

Set up log directory.
```{r}
  dir.create(opt$log_dir,showWarnings = FALSE)
  capture.output(opt, file = file.path(opt$log_dir,'model_Opts.csv'))
```

First download the full datasets.
```{r,eval=FALSE}
  PharmacoGx::availablePSets()
  for (dataset in opt$datasets) {
    PharmacoGx::downloadPSet(dataset)
  }
```

Load data.
```{r}
  for (dataset in opt$datasets) {
    if (opt$run_on_cluster) {
      load(file.path('PSets',paste(dataset,'RData',sep='.')))
    } else {
      load(file.path('../PSets',paste(dataset,'RData',sep='.')))
    }
  }
  if (opt$use_small_datasets) {
    CCLE <- PharmacoGx::CCLEsmall
    GDSC <- PharmacoGx::GDSCsmall
  }
```

Format the sensitivity data for each experiment. Find cells and drugs assayed across experiment. Remove noisy experiments and mislabelled cell lines. Calculate sensitivity measures per cell/drug.
```{r}
  intersection.tibble.list <- intersectPSetWrapper(datasets = opt$datasets,
                                                  minimum_intersection = opt$min_intersection,
                                                  intersectOn = c("drugs", "cell.lines"),
                                                  sensitivity_measure = opt$sensitivity_measure,
                                                  remove_noisy_curves = FALSE,
                                                  remove_mislabelled_cells = FALSE)
  intersection.tibble.list <- list(do.call(bind_rows,intersection.tibble.list))
  names(intersection.tibble.list) <- paste(opt$datasets,collapse='_')
```

Initialize drug and cell assignments for EM using prior specifications for probability sensitive and probability drug is broadly active. Or use a flat prior (random initialization).
```{r}
drugs.tibble.list <- lapply(intersection.tibble.list, function(li) {
  drug_dat <- li %>% 
    mutate(all_median = quantile(value,opt$prior.sensitive),
           all_mad = stats::mad(value),
           drug=as.factor(drug)) %>% 
    group_by(drug) %>% 
    mutate(median=median(value),
           mad=stats::mad(value),
           all_median=first(all_median),
           all_mad=first(all_mad)) %>%
    ungroup() %>%
    mutate(drug_type = ifelse(median<=all_median & mad<=all_mad,'targeted','broad')) %>%
    distinct(drug, drug_type, all_median, all_mad, median, median, mad)
  li %>% 
    left_join(drug_dat, by='drug') %>%
    mutate(sensitive = ifelse(value > all_median, 1,0)) %>%
    group_by(drug, measure, drug_type) %>%
    summarise(p_prior = mean(sensitive),
              #p_prior = median(value),
              sensitive = sum(sensitive),
              cell_count = n()) %>%
    ungroup() %>% 
    select(drug, measure, p_prior, sensitive, cell_count, drug_type)
})
cells.tibble.list <- lapply(1:length(intersection.tibble.list), function(li) {
  intersection.tibble.list[[li]] %>% 
    left_join(drugs.tibble.list[[li]], by=c('drug','measure')) %>% 
    select(drug:measure,drug_type) %>%
    ungroup() %>% 
    group_by(experiment) %>%
    mutate(prior_threshold = quantile(value,probs = opt$prior.sensitive), 
           cell_type = ifelse(value>=prior_threshold,'sensitive','resistant')) %>%
    ungroup()
})
names(cells.tibble.list) <- names(drugs.tibble.list)
```

Plot median versus median absolute deviation for joined data using the MAD and 60th percentile for drug-type classification.
```{r}
  for (meas in opt$sensitivity_measure) {
    dir.create(file.path(opt$log_dir,meas),showWarnings = FALSE)
    for (comp in names(intersection.tibble.list)) {
      dir.create(file.path(opt$log_dir,meas,comp),showWarnings = FALSE)
      p <- intersection.tibble.list[[comp]] %>%
        filter(measure==meas) %>%
        mutate(all_median = quantile(value,.6),
               all_mad = stats::mad(value),
               drug=as.factor(drug)) %>% 
        group_by(drug) %>% 
        mutate(median=median(value),
                  mad=stats::mad(value),
                  all_median=first(all_median),
                  all_mad=first(all_mad)) %>%
        ungroup() %>%
        mutate(broad = ifelse(median<=all_median & mad<=all_mad,'Narrow effect','Broad effect'),
               broad_hk = ifelse(mad>.13,'Broad effect','Narrow effect')) %>%
        ggplot(aes(x=median,y=mad,color=broad,shape=broad_hk,label=drug),size=3) + 
        geom_point() +
        geom_hline(aes(yintercept=.13),lty=2, color=2) + 
        geom_segment(aes(x=all_median, xend=all_median,y=-Inf,yend=all_mad),lty=2,color=1) + 
        geom_segment(aes(x=-Inf, xend=all_median,y=all_mad,yend=all_mad),lty=2,color=1) + 
        theme_bw() +
        scale_color_brewer(palette='Dark2') #+
        #facet_wrap(vars(experiment))
      ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('Median_v_MAD_p60.pdf',sep='')),
             width = 14, height = 8, units = "in",limitsize=FALSE)
      saveRDS(p, file=file.path(opt$log_dir,meas,comp,paste('Median_v_MAD_p60.RDS',sep='')))
    }
  }
```

Plot the drug and cell initial assignments.
```{r,eval=FALSE}
  common.drugs <- lapply(names(intersection.tibble.list), function(comp) {
    intersection.tibble.list[[comp]] %>%
      distinct(drug) %>% 
      pull()
  })
  names(common.drugs) <- names(intersection.tibble.list)
  for (meas in opt$sensitivity_measure) {
    for (comp in names(intersection.tibble.list)) {
      p <- drugs.tibble.list[[comp]] %>%
        filter(measure==meas) %>%
        ggplot(aes(p_prior)) +
          stat_bin(bins=50) + 
          theme_bw() + 
          theme(strip.text.x = element_text(size = 12),
            legend.position='none',
            axis.text=element_text(size=12),
            axis.title=element_text(size=12),
            legend.text=element_text(size=12),
            legend.title=element_text(size=12),
            title=element_text(size=14)) +
          coord_cartesian(xlim = c(0, 1)) +
          scale_x_continuous(name = 'p_prior') 
      ggsave(p, file=file.path(opt$log_dir,meas,comp,paste('p_prior.pdf',sep='')),width = 4, height = 4, units = "in",limitsize=FALSE)
      saveRDS(p, file=file.path(opt$log_dir,meas,comp,paste('p_prior.RDS',sep='')))
    }
  }
  for (meas in opt$sensitivity_measure) {
    for (comp in names(intersection.tibble.list)) {
      p <-  cells.tibble.list[comp] %>%
        bind_rows() %>%
        filter(measure==meas, drug %in% common.drugs[[comp]]) %>%
        mutate(drug=as.factor(drug)) %>% 
        mutate(drug=reorder(drug, value, mean)) %>%
        ggplot(aes(y=value,x=drug,fill=as.factor(drug_type))) +
          geom_boxplot() + 
          theme_bw() + 
          facet_wrap(vars(experiment), scales = 'free_x',ncol=1) + 
            theme(strip.text.x = element_text(size = 18),
            legend.position='bottom',
            axis.text=element_text(size=12),
            axis.text.y=element_text(size=16),
            axis.title=element_text(size=18),
            legend.text=element_text(size=12),
            axis.text.x = element_text(angle = 45, hjust = 1),
            legend.title=element_text(size=12),
            title=element_text(size=14)) + 
            scale_y_continuous(breaks=c(0,1)) +
            labs(x="Drug",y=NULL)
      ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('boxplot_raw_all_cells_prior.pdf',sep='')),width = 12, height = 8, units = "in",limitsize=FALSE)
      saveRDS(p, file=file.path(opt$log_dir,meas,comp,paste('boxplot_raw_all_cells_prior.RDS',sep='')))
      maxdr <- intersection.tibble.list[] %>%
        bind_rows() %>%
        filter(measure==meas, drug %in% common.drugs[[comp]]) %>%
        summarise(max(nchar(drug))) %>%
        pull()
      p <- cells.tibble.list[comp] %>%
        bind_rows() %>%
        filter(measure==meas) %>%
        mutate(color = ifelse(drug %in% common.drugs[[comp]],'blue','grey')) %>%
        mutate(drug=as.factor(drug),color=as.factor(color)) %>% 
        mutate(drug=reorder(drug, value, mean)) %>%
        ggplot(aes(y=value,x=drug)) +
          geom_boxplot(aes(color=color, fill=as.factor(drug_type)),show.legend=FALSE) + 
          theme_bw() + 
          facet_wrap(vars(experiment), scales = 'free_x',ncol=1) + 
            theme(strip.text.x = element_text(size = 18),
            legend.position='bottom',
            axis.text=element_text(size=16),
            axis.text.x =element_text(colour = 'white',angle = 45, hjust = 1,size=8),
            axis.title=element_text(size=18),
            legend.text=element_text(size=12),
            legend.title=element_text(size=12),
            title=element_text(size=14)) + 
            labs(x="Drug",y=meas) + 
            scale_y_continuous(breaks=c(0,1)) +
            scale_color_manual(values=c('black','grey50')) 
      ggsave(p,file=file.path(opt$log_dir,meas,comp,paste('boxplot_raw_all_drugs_prior.pdf',sep='')),width = 12, height = 8, units = "in",limitsize=FALSE)
      saveRDS(p, file=file.path(opt$log_dir,meas,comp,paste('boxplot_raw_all_drugs_prior.RDS',sep='')))
    }
  }
```

Using the assignments, fit distributions (first M step) and use these as priors to initialize EM with. Alternatively, use prior specification for all drug parameters.
```{r}
meas <- opt$sensitivity_measure[1]
drug_types_list <- lapply(drugs.tibble.list, function(tibb) {
  tibb %>%
    filter(measure==meas) %>%
    group_by(drug_type) %>%
    do(mutate(fit_bb_mle(.$sensitive, .$cell_count), number = nrow(.))) %>%
    ungroup() %>%
    mutate(drug_type_prior = number / sum(number)) 
})
targetted_drug_fits_list <- lapply(cells.tibble.list, function(tibb) {
  ttibb <- tibb %>%
    filter(measure==meas) %>%
    mutate(value = ifelse(value==0,1e-3,value)) %>%
    mutate(drug_type = 'targeted') %>%
    group_by(drug, cell_type, drug_type, experiment) %>%
    do(mutate(fit_beta_mle(.$value),number = nrow(.))) %>%
    group_by(drug, drug_type, experiment) %>%
    mutate(ndist=n_distinct(cell_type)) %>%
    ungroup()
  ttibb %>%
    bind_rows(
      ttibb %>% 
        filter(ndist<2) %>% 
        mutate(cell_type2 = case_when(cell_type=='resistant' ~ 'sensitive',cell_type=='sensitive' ~ 'resistant'),
               cell_type=cell_type2,
               number=0,
               alpha=case_when(cell_type == 'resistant' ~ .5,
                               cell_type == 'sensitive' ~ 50),
               beta=case_when(cell_type == 'resistant' ~ 7.5,
                              cell_type == 'sensitive' ~ 50)) %>%
        select(-cell_type2)
    ) %>%
    group_by(drug, experiment) %>%       
    mutate(targeted_cell_type_prior = number / sum(number)) %>%
    ungroup() %>% 
    select(-ndist)
})
broad_drug_fits_list <- lapply(cells.tibble.list, function(tibb) {
  tibb %>%
    filter(measure==meas) %>%
    mutate(x=ifelse(value==0,1e-3,value)) %>%
    group_by(drug, experiment) %>%
    do(mutate(fit_beta_mle(.$x),
              number = nrow(.),
              broad_cell_type_prior = mean(.$value>=.$prior_threshold))) %>%
    ungroup() %>% 
    mutate(drug_type = 'broad') %>%
    select(drug, drug_type, alpha, beta, number, broad_cell_type_prior, experiment)
})
```

Perform an expectation step using the distributions to initialize for the EM. 
```{r}
targetted_cell_assignments_list <- lapply(1:length(targetted_drug_fits_list), function(num) {
  targetted_drug_list <- unique(targetted_drug_fits_list[[num]]$drug)
  targetted_cell_assignments <- lapply(targetted_drug_list, function(dr) {
    cells.tibble.list[[num]] %>%
      filter(drug == dr,measure==meas) %>%
      select(drug:measure) %>%
      mutate(drug_type = 'targeted') %>%
      mutate(value=ifelse(value==0,1e-3,value)) %>%
      crossing(targetted_drug_fits_list[[num]] %>% filter(drug == dr) %>% select(-drug,-drug_type) %>% rename(experiment1=experiment)) %>%
      filter(experiment==experiment1) %>% 
      select(-experiment1) %>% 
      mutate(median = qbeta(.5,alpha,beta),
             likelihood = dbeta(value, alpha, beta)) %>% 
      group_by(cell_type) %>%
      mutate(max.likelihood=max(likelihood)) %>%
      ungroup() %>%
      mutate(likelihood = case_when(value>median & cell_type == 'sensitive' ~ max.likelihood-likelihood + max.likelihood, 
                                    value<median & cell_type == 'resistant' ~ max.likelihood-likelihood + max.likelihood, 
                                    TRUE~likelihood)) %>%
      mutate(likelihood = targeted_cell_type_prior * likelihood) %>%
      group_by(drug, cell, experiment) %>%
      mutate(posterior=exp(log(likelihood)-log(sum(likelihood)))) %>% 
      top_n(1, likelihood) %>%
      ungroup()
  })
  do.call(bind_rows, targetted_cell_assignments)
})
broad_cell_assignments_list <- lapply(1:length(broad_drug_fits_list), function(num) {
  cells.tibble.list[[num]] %>%
      filter(drug %in% unique(broad_drug_fits_list[[num]]$drug),measure==meas) %>%
      select(drug:measure) %>%
      mutate(drug_type = 'broad') %>%
      mutate(value=ifelse(value==0,1e-3,value)) %>%
      left_join(broad_drug_fits_list[[num]], by=c('drug','drug_type', 'experiment')) %>%
      mutate(likelihood = dbeta(value, alpha, beta),
             cell_type = ifelse((broad_cell_type_prior*pbeta(value, alpha, beta)) >
                                  ((1-broad_cell_type_prior)*(1-pbeta(value, alpha, beta))),
                                'sensitive','resistant'))
})
drugs.tibble.list <- lapply(1:length(drugs.tibble.list), function(num) {
  targetteds <- drugs.tibble.list[[num]] %>%
    filter(measure==meas) %>%
    select(drug, measure) %>%
    right_join(targetted_cell_assignments_list[[num]] %>% select(drug, cell, cell_type, likelihood), by='drug') %>% 
    group_by(drug, measure) %>%
    summarise(sensitive = sum(cell_type=='sensitive'),
              cell_count = n()) %>%
    ungroup() %>% 
    mutate(type='targeted')
  broads <- drugs.tibble.list[[num]] %>%
    filter(measure==meas) %>%
    select(drug, measure) %>%
    right_join(broad_cell_assignments_list[[num]] %>% select(drug, cell, cell_type), by='drug') %>% 
    group_by(drug, measure) %>%
    summarise(sensitive = sum(cell_type=='sensitive'),
              cell_count = n()) %>%
    ungroup() %>%
    mutate(type='broad')
  bind_rows(targetteds, broads)
})
drug_assignments_list <- lapply(1:length(drugs.tibble.list), function(num) {
  drugs.tibble.list[[num]] %>%
    filter(measure==meas) %>%
    rename(drug_type = type) %>%
    right_join(drug_types_list[[num]] %>% select(-number), by='drug_type') %>%
    mutate(likelihood = drug_type_prior * VGAM::dbetabinom.ab(sensitive, cell_count, alpha, beta)) %>%
    group_by(drug) %>%
    mutate(posterior=likelihood/sum(likelihood)) %>% 
    top_n(1, likelihood) %>%
    ungroup()
})
cell_assignments_list <- lapply(1:length(targetted_cell_assignments_list), function(num) {
  bind_rows(targetted_cell_assignments_list[[num]],broad_cell_assignments_list[[num]]) %>%
    group_by(drug, cell_type, experiment) %>%
    fill(targeted_cell_type_prior, .direction='down') %>%
    ungroup() %>%
    group_by(drug, experiment) %>% 
    fill(broad_cell_type_prior, .direction='up') %>%
    ungroup() %>% 
    right_join(drug_assignments_list[[num]] %>% select(drug, drug_type), by=c('drug','drug_type')) %>% 
    select(drug, cell, value, experiment, measure, drug_type, cell_type, broad_cell_type_prior, targeted_cell_type_prior)
})
names(cell_assignments_list) <- names(drug_types_list)
```

Run EM.
```{r}
  iterations_list <- list()
  for(num in 1:length(cell_assignments_list)) {
    drug_assignments <- drug_assignments_list[[num]]
    cell_assignments <- cell_assignments_list[[num]]
    iterations_list[[num]] <- accumulate(1:100, iterate_em, .init = list(drug_assignments = drug_assignments,
                                                                       cell_assignments = cell_assignments))
  }
  names(iterations_list) <- names(intersection.tibble.list)
```

Obtain posterior information from last EM rep.
```{r}
  posterior_drug_types_list <- lapply(names(iterations_list), function(num) {
    iterations_list[[num]] %>% 
      map_df("drug_types", .id = "iteration") %>% 
      filter(iteration==max(iteration)) 
  })
  posterior_drug_assignments_list <- lapply(names(iterations_list), function(num) {
    iterations_list[[num]] %>% 
      map_df("drug_assignments", .id = "iteration") %>% 
      filter(iteration==max(iteration))
  })
  posterior_drug_fits_list <- lapply(names(iterations_list), function(num) {
    iterations_list[[num]] %>% 
      map_df("drug_fits", .id = "iteration") %>% 
      filter(iteration==max(iteration))
  })
  posterior_cell_assignments_list <- lapply(names(iterations_list), function(num) {
    iterations_list[[num]] %>% 
      map_df("cell_assignments", .id = "iteration") %>% 
      filter(iteration==max(iteration))
  })
  names(posterior_cell_assignments_list) <- names(iterations_list)
```

Plot the posterior drug densities.
```{r,eval=TRUE}  
drug_posteriors_proportions <- lapply(names(posterior_cell_assignments_list), function(ii) {
  posterior_cell_assignments_list[[ii]] %>%
    group_by(drug) %>%
    summarise(posterior = sum(cell_type=='sensitive')/n()) %>%
    ungroup()
}) 
names(drug_posteriors_proportions) <- names(iterations_list)

for (num in names(iterations_list)) {
  drug_type_iterations <- iterations_list[[num]] %>% 
    map_df("drug_types", .id = "iteration") %>% 
    bind_rows(drug_types_list[[num]] %>% 
                mutate(iteration='0')) %>%
    group_by(iteration) %>%
    mutate(drug_type_prior = case_when(is.na(drug_type_prior) ~ number/sum(number), TRUE ~ drug_type_prior)) %>%
    ungroup()
  drug_fits_iterations <- iterations_list[[num]] %>% 
    map_df("drug_fits", .id = "iteration") %>% 
    bind_rows(broad_drug_fits_list[[num]] %>% 
                mutate(iteration='0') %>%
                select(drug, drug_type, alpha, beta, iteration),
              targetted_drug_fits_list[[num]] %>% 
                mutate(iteration='0') %>%
                select(drug, drug_type, alpha, beta, iteration))
  cell_assignments_iterations <- iterations_list[[num]] %>% 
    map_df("cell_assignments", .id = "iteration") %>% 
    bind_rows(cell_assignments_list[[num]] %>%
                mutate(iteration='0'))
  betadens <- drug_fits_iterations %>%
    filter(iteration==max(iteration)) %>%
    mutate(cross = paste(cell_type, drug, experiment, sep='_')) %>%
    plyr::ddply(., "cross", function(df) {
      data.frame( 
      value = seq(.001, .999, length = 1000),
      beta_curve = dbeta(seq(.001, .999, length = 1000), 
                           df$alpha, 
                           df$beta) 
    )
  })
  betadens <- as_tibble(betadens) %>% 
    separate(cross,into=c('cell_type','drug','experiment'),sep='_') %>%
    full_join(drug_fits_iterations %>% mutate(cell_type = ifelse(is.na(cell_type),'NA',cell_type)), by=c('drug','cell_type','experiment')) %>%
    left_join(drug_posteriors_proportions[[num]], by='drug') %>%
    mutate(posterior = ifelse(drug_type=='broad',1,posterior)) %>%
    mutate(posterior = ifelse(drug_type=='targeted' & cell_type=='resistant',1,posterior)) %>%
    group_by(drug,cell_type, experiment) %>% 
    #mutate(prior = ifelse(prior < .1,.1,prior)) %>%
    mutate(beta_curve = beta_curve/max(beta_curve)*posterior) %>%
    ungroup() %>%
    filter(iteration==max(iteration)) %>%
    mutate(cell_type = ifelse(cell_type=='sensitive','sensitive','resistant'))
  nummdrs <- betadens %>% summarise(n_distinct(drug)) %>% pull()
  drs_array <- betadens %>% distinct(drug) %>% pull()
  seeqq <- seq(1,nummdrs,by=16)
  
  p <- cell_assignments_iterations %>%
    filter(iteration==max(iteration)) %>%
    ggplot(aes(value,y=..scaled..)) +
      geom_density(adjust=.5,fill=1) +
      theme_bw() + 
      facet_wrap(vars(drug), scales = 'free_y',ncol=3) + 
      theme(strip.text.x = element_text(size = 8),
          legend.position='none',
          axis.text=element_text(size=12),
          axis.title=element_text(size=12),
          legend.text=element_text(size=12),
          legend.title=element_text(size=12),
          title=element_text(size=14)) + 
    scale_x_continuous(limits = c(0,1), name=meas) + 
    geom_line(data=betadens, aes(y = beta_curve, color=cell_type, lty=experiment), lwd = 1) 
  ggsave(p, file=file.path(opt$log_dir,meas,num,paste('fitted_densities_smoothed.pdf',sep='')),width = 12, height = 24, units = "in")
  saveRDS(p, file=file.path(opt$log_dir,meas,num,paste('fitted_densities_smoothed.RDS',sep='')))
  while(dev.cur()!=1) {dev.off()}
  dir.create(file.path(opt$log_dir,meas,num,'fitted_densities_by_drug'),showWarnings = FALSE)
  for (dr in unique(cell_assignments_iterations$drug)) {
    dr_type <- cell_assignments_iterations %>%
      filter(iteration==max(iteration),drug==dr) %>% 
      distinct(drug_type) %>% 
      pull
    dr_short <- gsub("[^[:alnum:]]","",dr)
    dr_nonums <- gsub('[0-9]+', '', dr_short)
    if (nchar(dr_nonums)==0) {dr_short <- paste('drug',dr_short,sep='')}
    p <- cell_assignments_iterations %>%
      filter(iteration==max(iteration),drug==dr) %>%
      ggplot(aes(value,y=..scaled..)) +
        geom_density(adjust=.5,fill=1) +
        theme_bw() + 
        facet_grid(cols=vars(experiment)) +
        theme(strip.text.x = element_text(size = 18),
          legend.position='none',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=16),
          legend.title=element_text(size=16),
          title=element_text(size=18)) +
      scale_x_continuous(limits = c(0,1)) + 
      labs(y='Scaled Density',x='AOC') +
      geom_line(data=betadens %>% filter(drug==dr), aes(y = beta_curve, color=cell_type), lwd = 1.5) +
      ggtitle(paste(dr,sep=' '))
    ggsave(file=file.path(opt$log_dir,meas,num,'fitted_densities_by_drug',paste(dr_short,'.png',sep='')),width = 12, height = 4, units = "in")
    saveRDS(p, file.path(opt$log_dir,meas,num,'fitted_densities_by_drug',paste(dr_short,'.RDS',sep='')))
  }
}
```

Extract intersection data.
```{r}
  intersection.fitted.list <- lapply(iterations_list, function(num) {
    num %>%
      map_df("cell_assignments", .id = "iteration") %>%
      filter(iteration == max(iteration)) %>%
      group_by(cell, drug, measure) %>%
      filter(n_distinct(experiment)>1) %>%
      ungroup()
  })
```

Format posterior agreements.
```{r}
  posterior_drug_types <- do.call(bind_rows,posterior_drug_types_list) 
  posterior_drug_assignments <- do.call(bind_rows,posterior_drug_assignments_list) 
  posterior_drug_fits <-  do.call(bind_rows,posterior_drug_fits_list) 
  posterior_cell_assignments <- do.call(bind_rows,posterior_cell_assignments_list) 
```

Save posteriors.
```{r}
saveRDS(object=posterior_drug_types,file=file.path(opt$log_dir,'posterior_drug_types.RDS'))
saveRDS(object=posterior_drug_fits,file=file.path(opt$log_dir,'posterior_drug_fits.RDS'))
saveRDS(object=posterior_drug_assignments,file=file.path(opt$log_dir,'posterior_drug_assignments.RDS'))
saveRDS(object=posterior_cell_assignments,file=file.path(opt$log_dir,'posterior_cell_assignments.RDS'))
saveRDS(object=intersection.fitted.list,file=file.path(opt$log_dir,'intersection.fitted.list.RDS'))
```

Format a big data frame with all relevant posterior information.
```{r}
posterior_cell_assignments <- readRDS(file=file.path(opt$log_dir,'posterior_cell_assignments.RDS'))
posterior_drug_assignments <- readRDS(file=file.path(opt$log_dir,'posterior_drug_assignments.RDS'))

posterior <- posterior_cell_assignments %>%
  select(drug, cell, experiment, drug_type, cell_type, posterior, likelihood, value) %>%
  rename(cell_type_posterior=posterior,
         cell_type_likelihood=likelihood,
         realized_value=value) %>%
  group_by(drug, cell) %>% 
  mutate(num_experiments = n_distinct(experiment)) %>%
  ungroup() %>%
  left_join(posterior_drug_assignments %>%
              select(drug, drug_type, posterior,likelihood) %>%
              rename(drug_type_posterior=posterior,
                     drug_type_likelihood=likelihood), by=c('drug_type','drug')) %>%
  mutate(cell_type = ifelse(cell_type == 'sensitive' & drug_type == 'broad',
                            'resistant',cell_type)) %>% #filter(drug==dr) %>% View
  mutate(cell_type_posterior = ifelse((cell_type == 'resistant' & drug_type == 'targeted') | drug_type=='broad',
                                      1-cell_type_posterior,cell_type_posterior)) %>%
  mutate(drug_type_posterior = ifelse(drug_type == 'broad', 1-drug_type_posterior,drug_type_posterior)) %>%
  rename(posterior_probability_sensitive = cell_type_posterior,
         posterior_probability_targeted = drug_type_posterior)
saveRDS(object=posterior,file=file.path(opt$log_dir,'posterior.formatted.RDS'))
```

Plots the posterior probability against the observed sentivity metric, facetted by study/experiment.
```{r}
dir.create(file.path(opt$log_dir,'posterior_sensitivity_comparisons'),showWarnings = FALSE)
posterior <- readRDS(file.path(opt$log_dir,'posterior.formatted.RDS'))
expit <- function(x) {
  return(1/(1+exp(-x)))
}
dr <- '681640'
for (dr in unique(posterior$drug)) {
  tdat <- posterior %>%
    filter(drug==dr) %>%
    select(cell,cell_type,num_experiments,posterior_probability_sensitive, experiment, realized_value) 
  dr_short <- gsub("[^[:alnum:]]","",dr)
  dr_nonums <- gsub('[0-9]+', '', dr_short)
  if (nchar(dr_nonums)==0) {dr_short <- paste('drug',dr_short,sep='')}
  ylabb <- ifelse(tdat %>% summarise(n_distinct(cell_type)) %>% pull == 2,'Probability(cell is sensitive)','Cell sensitivity CDF')
  p <- tdat %>%
    ggplot(aes(x=realized_value,y=posterior_probability_sensitive)) + 
    geom_point(aes(color=as.factor(num_experiments),shape=cell_type),size=3,alpha=.6) + 
    geom_hline(aes(yintercept=.5),lty=2) +
    geom_vline(aes(xintercept=.2),lty=2,alpha=.5,color='red') + 
    geom_smooth(data=subset(tdat, num_experiments==1), method = "nls", 
              method.args = list(formula = y ~ expit(a*x+b), start = list(a=0,b=0)),se = FALSE,color='grey90') +
    facet_wrap(vars(experiment)) + 
    theme_bw() + 
    scale_color_brewer(palette = 'Dark2') + 
    theme(legend.position='bottom') + 
    ylab(ylabb) + 
    xlab('Observed Area-above-the-curve') + 
    guides(color=guide_legend(title="Number experiments"),
           shape=guide_legend(title="Cell type"))
  ggsave(p,file=file.path(opt$log_dir,'posterior_sensitivity_comparisons',paste(dr_short,'.pdf',sep='')),width=8,height=5,units='in')
  saveRDS(p, file.path(opt$log_dir,'posterior_sensitivity_comparisons',paste(dr_short,'.RDS',sep='')))
  while(dev.cur()!=1) {dev.off()}
}
```

Plot the posterior probability ranking the cell sensitivity per drug, along with error bars. 
```{r}
dir.create(file.path(opt$log_dir,'posterior_sensitivity_waterfalls'),showWarnings = FALSE)
posterior <- readRDS(file.path(opt$log_dir,'posterior.formatted.RDS'))
dr <- 'Crizotinib'
for (dr in unique(posterior$drug)) {
  tdat <- posterior %>%
    filter(drug==dr)
  xlabb <- ifelse(tdat %>% summarise(n_distinct(cell_type)) %>% pull == 2,'Probability(cell is sensitive)','Cell sensitivity CDF')
  dr_short <- gsub("[^[:alnum:]]","",dr)
  dr_nonums <- gsub('[0-9]+', '', dr_short)
  if (nchar(dr_nonums)==0) {dr_short <- paste('drug',dr_short,sep='')}
  tdat <- tdat %>%
    mutate(sd=posterior_probability_sensitive*(1-posterior_probability_sensitive)/sqrt(num_experiments)) %>% 
    distinct(cell, cell_type, num_experiments, posterior_probability_sensitive, sd) %>%
    rename(point=posterior_probability_sensitive) %>%
    mutate(point=round(point,digits=4), sd=round(sd,digits=4)) %>%
    group_by(point, num_experiments, sd) %>%
    summarise(cell=first(cell),
              count=n()) %>%
    ungroup() %>%
    mutate(cell =  reorder(cell, -point),
           lowerci=point-sd,
           upperci=point+sd)
  p <- tdat %>%
    ggplot(aes(y=cell, x=point, color=as.factor(num_experiments),size=count)) +
    geom_point(alpha=.6) + 
    geom_errorbarh(aes(xmin=lowerci, xmax=upperci), height=.1,alpha=.25, show.legend=FALSE) +
    geom_vline(aes(xintercept=.5),lty=2,alpha=.5,color='red') + 
    theme_bw() + 
    scale_color_brewer(palette = 'Dark2') + 
    theme(legend.position='bottom',
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid.major.y = element_blank(), panel.grid.minor.y = element_blank()) + 
    ylab('Cell line') + 
    xlab(xlabb) + 
    guides(color=guide_legend(title="Number experiments"),
           size=guide_legend(title="Count"))
  ggsave(p,file=file.path(opt$log_dir,'posterior_sensitivity_waterfalls',paste(dr_short,'.pdf',sep='')),width=10,height=8,units='in')
  saveRDS(p, file.path(opt$log_dir,'posterior_sensitivity_waterfalls',paste(dr_short,'.RDS',sep='')))
  while(dev.cur()!=1) {dev.off()}
}
```

Output table of sensitivities.
```{r, eval=FALSE}
library(knitr)
library(kableExtra)
library(xlsx)
posterior <- readRDS(file.path(opt$log_dir,'posterior.formatted.RDS'))
dir.create(file.path(opt$log_dir,'posterior_sensitivity_tables'),showWarnings = FALSE)
dr <- 'Crizotinib'
for (dr in unique(posterior$drug)) {
  dr_short <- gsub("[^[:alnum:]]","",dr)
  dr_nonums <- gsub('[0-9]+', '', dr_short)
  if (nchar(dr_nonums)==0) {dr_short <- paste('drug',dr_short,sep='')}
  tdat <- posterior %>%
    filter(drug==dr) %>%
    distinct(drug, drug_type, cell, cell_type, num_experiments, posterior_probability_sensitive, realized_value, experiment) %>%
    rename(sensitivity=posterior_probability_sensitive) %>%
    spread(experiment, realized_value) %>%
    arrange(desc(sensitivity))
  tdat %>%
    kable(caption=dr) %>%
    kable_styling(bootstrap_options = c("striped", "hover")) %>%
    scroll_box(width = "100%", height = "100%") %>%
    save_kable(file = file.path(opt$log_dir,'posterior_sensitivity_tables',paste(dr_short,'.html',sep='')), self_contained = TRUE)
    write.xlsx(as.data.frame(tdat), file.path(opt$log_dir,'posterior_sensitivity_tables','posterior_estimates.xlsx'),
               sheetName = 'dr', col.names = TRUE, row.names = FALSE, append = TRUE)
}
```

Posterior drug type density plot.
```{r}
p <- posterior_drug_types %>% 
  crossing(x = seq(.001, .999, .001)) %>%
  mutate(posterior = number/sum(number)) %>%
    mutate(density = posterior * dbeta(x, alpha, beta)) %>%
    ggplot(aes(x, density, color = drug_type, group = drug_type)) +
    geom_line() +
    theme_bw() + 
        theme(strip.text.x = element_text(size = 18),
          legend.position='bottom',
          axis.text=element_text(size=16),
          axis.title=element_text(size=18),
          legend.text=element_text(size=18),
          legend.title=element_text(size=18),
          title=element_text(size=18)) +
    labs(colour="Drug Type",y='Density',x='AOC') + 
    scale_x_continuous(limits = c(0,1), breaks=c(0,.5,1)) + 
    ggtitle('Posterior Drug-Type Densities')
  ggsave(p, file=file.path(opt$log_dir,meas,paste('posterior_drug_types.pdf',sep='')),width = 12, height = 8, units = "in")
  saveRDS(p, file.path(opt$log_dir,meas,paste('posterior_drug_types.RDS',sep='')))
```

Clear environment.
```{r}
rm(list=ls(all.names = TRUE))
```

