---
title: "Untitled"
author: "Matt Ploenzke"
date: "8/12/2019"
output: html_document
---

```{r}
library(PharmacoGx)
library(readxl)
library(tidyverse)
library(caret)
library(randomForest)
library(mlbench)
```

Load data and filter to drug.
```{r}
drug_for_biomarkers <- 'lapatinib'
min_posterior_probability_sensitive <- .25
log_dir <- 'biomarkers_plots'
dir.create(log_dir,showWarnings = FALSE)
use_all_features <- FALSE
use_known_drug_features <- TRUE
posterior <- readRDS('~/Desktop/Concordance/tidyPharmaco/CCLE_GDSC_fit_joint/posterior.formatted.RDS') %>%
#posterior <- readRDS('~/concordance/posterior.formatted.RDS') %>%
  filter(drug==drug_for_biomarkers) %>%
  select(cell, experiment, cell_type, posterior_probability_sensitive)
datasets <- posterior %>% distinct(experiment) %>% pull()
gene_drug_asociations <- read_excel('~/Desktop/Concordance/PSets/gene_drug_asociations.xlsx', sheet = "mutation") %>%
#gene_drug_asociations <- read_excel('~/concordance/PSets/gene_drug_asociations.xlsx', sheet = "mutation") %>%
  as_tibble() %>%
  bind_rows(read_excel('~/Desktop/Concordance/PSets/gene_drug_asociations.xlsx', sheet = "copy_number_variation"),
            read_excel('~/Desktop/Concordance/PSets/gene_drug_asociations.xlsx', sheet = "expression")) %>%
  #bind_rows(read_excel('~/concordance/PSets/gene_drug_asociations.xlsx', sheet = "copy_number_variation"),
  #          read_excel('~/concordance/PSets/gene_drug_asociations.xlsx', sheet = "expression")) %>%
  mutate(type=case_when(type=='expression' ~ 'rna',
                        type=='copy_number_variation' ~ 'cnv',
                        TRUE ~ type)) %>%
  rename(drug=compound) %>%
  select(type, drug, gene, source)
if (use_known_drug_features) {
  gene_drug_asociations <- gene_drug_asociations %>% filter(drug==drug_for_biomarkers)
}
```

Set up X and Y data matrices.
```{r}
rez <- list()
for (dataset in datasets) {
  load(file.path('~/Desktop/Concordance/PSets',paste(dataset,'RData',sep='.')))
  #load(file.path('~/concordance/PSets',paste(dataset,'RData',sep='.')))
  eval(parse(text = paste('tempPset <- ',dataset,sep='')))
  y_new_temp <- summarizeSensitivityProfiles(tempPset, sensitivity.measure = 'auc_recomputed', summary.stat = 'median', verbose = FALSE) %>%
    as.data.frame() %>%
    rownames_to_column('drug') %>%
    as_tibble() %>% 
    filter(drug==drug_for_biomarkers) %>%
    gather(key='cell',value='value',-drug) %>%
    filter(!is.na(value)) %>%
    mutate(waterfall=PharmacoGx:::callingWaterfall(value,type='AUC')) %>%
    ungroup() %>% 
    rename(auc_recomputed=value) %>%
    mutate(naive=ifelse(auc_recomputed>.2,'sensitive','resistant')) %>%
    mutate(experiment = dataset)
  for (feat in c('cnv','rna','mutation')) {
    features <- gene_drug_asociations %>%
      filter(type==feat) %>%
      distinct(gene) %>% 
      pull()
    if (use_all_features) {
      idx <- 1:length(featureInfo(tempPset,feat)$Symbol)
    } else {
      idx <- which(featureInfo(tempPset,feat)$Symbol %in% features)
    }
    molfeatures <- fNames(tempPset, feat)[idx]
    if (length(molfeatures) > 0) {
      stat <- ifelse(feat=='mutation','and','median')
      x_new <- summarizeMolecularProfiles(tempPset, mDataType = feat, summary.stat = stat, verbose=TRUE) %>%
        Biobase::exprs() %>%
        as.data.frame() %>%
        rownames_to_column('gene') %>%
        as_tibble() %>%
        gather(cell, value, -gene) %>%
        filter(gene %in% molfeatures) %>%
        mutate(gene = paste(gene,feat,sep='_')) %>%
        spread(gene, value) %>% 
        na.omit() 
    } else {
      x_new <- tibble(cell='NA')
    }
    if (feat=='cnv') {
      joined <- x_new 
    } else {
      joined <- x_new %>% full_join(joined,by='cell')
    }
  }
  rez[[dataset]] <- joined %>% inner_join(y_new_temp, by='cell')
  eval(parse(text=paste('rm(',dataset,',tempPset, x_new, joined, y_new_temp)',sep='')))
}
rez <- do.call(bind_rows, rez)
rez <- rez %>% 
  mutate_at(vars(contains('mutation')),funs(as.numeric)) %>%
  mutate_at(vars(contains('cnv')),funs(as.numeric)) %>%
  mutate_at(vars(contains('rna')),funs(as.numeric))

# filter columns with all NA in a single experiment
for (vvar in colnames(rez)) {
  max_na <- rez %>% 
    group_by(experiment) %>% 
    summarize(tt = mean(is.na(!!sym(vvar)))) %>%
    ungroup() %>%
    pull(tt) %>%
    max
  if (max_na == 1) {
    rez <- rez %>% select(-!!sym(vvar))
  }
}
rez <- rez %>%
  inner_join(posterior,by=c('cell','experiment')) %>% 
  mutate(cell_type = case_when(posterior_probability_sensitive > min_posterior_probability_sensitive ~ 'sensitive',TRUE ~ 'resistant')) %>%
  mutate_at(vars(contains('cnv')),funs( if_else( is.na(.), mean(.,na.rm=TRUE), .))) %>%
  mutate_at(vars(contains('rna')),funs( if_else( is.na(.), mean(.,na.rm=TRUE), .))) %>%
  mutate_at(vars(contains('mutation')),funs( if_else( is.na(.), mean(.,na.rm=TRUE), .)))
```

Define custom random forest caret method.
```{r}
customRF <- list(type = "Classification", library = "randomForest", loop = NULL)
customRF$parameters <- data.frame(parameter = c("mtry", "ntree"), class = rep("numeric", 2), label = c("mtry", "ntree"))
customRF$grid <- function(x, y, len = NULL, search = "grid") {}
customRF$fit <- function(x, y, wts, param, lev, last, weights, classProbs, ...) {
  randomForest(x, y, mtry = param$mtry, ntree=param$ntree, ...)
}
customRF$predict <- function(modelFit, newdata, preProc = NULL, submodels = NULL) {predict(modelFit, newdata)}
customRF$prob <- function(modelFit, newdata, preProc = NULL, submodels = NULL) {predict(modelFit, newdata, type = "prob")}
customRF$sort <- function(x) {x[order(x[,1]),]}
customRF$levels <- function(x) {x$classes}
```

Train models for varying outcome variables.
```{r}
metric <- "Accuracy"
set.seed(12345)
control <- trainControl(method="repeatedcv", number=10, repeats=3)
tunegrid <- expand.grid(.mtry=c(1:20), .ntree=c(10, 50, 100, 150))
all_acc <- tibble()
uncertain_points <- rez %>% filter(waterfall=='intermediate')
rez <- rez %>% filter(waterfall!='intermediate')
for (depVar in c('waterfall','naive','cell_type')) {
  x <- rez %>% 
    select(-drug, -cell, -experiment, -waterfall, -auc_recomputed, -naive, -cell_type, -posterior_probability_sensitive) %>% 
    select(ends_with('mutation'), ends_with('rna'), ends_with('cnv'))
  y <- rez %>% select(depVar)
  dataset <- y %>% 
    rename(Class=depVar) %>% 
    select(Class) %>% 
    bind_cols(x) %>% 
    na.omit() %>%
    mutate(Class = as.character(Class))
  print(nrow(dataset))
  custom <- train(Class~., data=dataset, method=customRF, metric=metric, tuneGrid=tunegrid, trControl=control)
  all_acc <- custom$results %>%
    as_tibble() %>% 
    mutate(outcome_variable=depVar) %>%
    bind_rows(all_acc)
}
```

Plot accuracy results.
```{r}
p <- all_acc %>% 
  mutate(ntree2 = ntree) %>%
  mutate(ntree = paste('Number trees: ', ntree, sep='')) %>%
  mutate(ntree = reorder(ntree,ntree2)) %>%
  mutate(outcome_variable = case_when(outcome_variable == 'cell_type' ~ 'P(sensitive | AAC) > 0.5',
                                      outcome_variable == 'naive' ~ 'AAC > 0.2',
                                      outcome_variable == 'waterfall' ~ 'Waterfall method')) %>%
  ggplot(aes(x=mtry,y=Kappa, color=outcome_variable, group=outcome_variable)) + 
  geom_point(alpha=.75) +
  geom_line(alpha=.75) + 
  facet_wrap(vars(ntree), ncol=4) +
  theme_bw() + 
  scale_color_brewer(palette='Dark2') + 
  labs(x='Number features', color='', y='',title='Random Forest Model Performance for Different Binarization Methods', subtitle='10-fold cross validation Cohens kappa') + 
  theme(legend.position = 'top')
ggsave(file.path(log_dir,'CV_kappas.pdf'), p)
saveRDS(p,file.path(log_dir,'CV_kappas.RDS'))

p <- all_acc %>% 
  mutate(ntree2 = ntree) %>%
  mutate(ntree = paste('Number trees: ', ntree, sep='')) %>%
  mutate(ntree = reorder(ntree,ntree2)) %>%
  mutate(outcome_variable = case_when(outcome_variable == 'cell_type' ~ 'P(sensitive | AAC) > 0.5',
                                      outcome_variable == 'naive' ~ 'AAC > 0.2',
                                      outcome_variable == 'waterfall' ~ 'Waterfall method')) %>%
  ggplot(aes(x=mtry,y=Accuracy, color=outcome_variable, group=outcome_variable)) + 
  geom_point(alpha=.75) +
  geom_line(alpha=.75) + 
  geom_errorbar(aes(ymin=Accuracy-AccuracySD, ymax=Accuracy+AccuracySD), width=.2, position=position_dodge(0.05),alpha=.75) + 
  facet_wrap(vars(ntree), ncol=4) +
  theme_bw() + 
  scale_color_brewer(palette='Dark2') + 
  labs(x='Number features', color='', y='',title='Random Forest Model Performance for Different Binarization Methods', subtitle='10-fold cross validation accuracy (Mean +/- SD)') + 
  theme(legend.position = 'top')
ggsave(file.path(log_dir,'CV_accuracy.pdf'), p)
saveRDS(p,file.path(log_dir,'CV_accuracy.RDS'))
```

Plot the relationship between three outcome measures.
```{r}
x <- rez %>% 
    select(-drug, -cell, -experiment, -waterfall, -auc_recomputed, -naive, -cell_type, -posterior_probability_sensitive) %>% 
    select(ends_with('mutation'), ends_with('rna'), ends_with('cnv'))
y <- rez %>% select(cell, experiment, auc_recomputed, waterfall, naive, posterior_probability_sensitive, cell_type) 
dataset <- y %>% 
  bind_cols(x) %>% 
  na.omit() %>% 
  select(cell, experiment, auc_recomputed, waterfall, naive, posterior_probability_sensitive, cell_type)
p <- dataset %>%
  ggplot(aes(x=auc_recomputed, y=posterior_probability_sensitive, color=waterfall)) + 
  geom_point() + 
  theme_bw() + 
  facet_grid(cols=vars(experiment)) +
  scale_color_brewer(palette='Dark2') + 
  geom_hline(aes(yintercept=min_posterior_probability_sensitive),lty=2) + 
  geom_vline(aes(xintercept=.2),lty=2)
ggsave(file.path(log_dir,'relationship_between_labels.pdf'), p)
saveRDS(p,file.path(log_dir,'relationship_between_labels.RDS'))
```

Fit best model for each outcome and compare features learned. 
```{r}
best_params <- all_acc %>% 
  group_by(outcome_variable) %>%
  filter(Accuracy==min(Accuracy)) %>%
  select(mtry, ntree, outcome_variable)
```

Start with the naive fit.
```{r}
x <- rez %>% 
    select(-drug, -cell, -experiment, -waterfall, -auc_recomputed, -naive, -cell_type, -posterior_probability_sensitive) %>% 
    select(ends_with('mutation'), ends_with('rna'), ends_with('cnv'))
y <- rez %>% select(cell, experiment, waterfall, naive, posterior_probability_sensitive, cell_type, auc_recomputed) 
dataset <- y %>% 
  bind_cols(x) %>% 
  na.omit() 

dataset_temp <- dataset %>% select(naive, ends_with('mutation'), ends_with('rna'), ends_with('cnv')) %>% mutate(naive=as.factor(naive))
fit1 <- randomForest(naive~.,data=dataset_temp,
                     ntree=pull(filter(best_params,outcome_variable=='naive'),ntree),
                     mtry=pull(filter(best_params,outcome_variable=='naive'),mtry))

naive_imp <- importance(fit1) %>%
  as.data.frame() %>%
  rownames_to_column('feature') %>% 
  as_tibble() %>%
  mutate(outcome_variable = 'naive')

naive_preds <- dataset_temp %>%
  select(naive) %>% 
  mutate(Outcome = 'naive') %>%
  rename(Actual=naive) %>%
  bind_cols(dataset %>% select(cell, experiment)) %>%
  mutate(Predicted=fit1$predicted)

naive_diagnostics <- confusionMatrix(naive_preds$Actual, naive_preds$Predicted)
```

Get test set (intermediate called by waterfall) predictions for this measure.
```{r}
x_test <- uncertain_points %>% 
    select(-drug, -cell, -experiment, -waterfall, -auc_recomputed, -naive, -cell_type, -posterior_probability_sensitive) %>% 
    select(ends_with('mutation'), ends_with('rna'), ends_with('cnv'))
y_test <- uncertain_points %>% select(cell, experiment, waterfall, naive, posterior_probability_sensitive, cell_type, auc_recomputed)
dataset_test <- y_test %>% 
  bind_cols(x_test) %>% 
  na.omit() 
dataset_test_temp <- dataset_test %>% select(naive, ends_with('mutation'), ends_with('rna'), ends_with('cnv')) %>% mutate(naive=as.factor(naive))
naive_test_preds <- dataset_test %>%
  select(waterfall) %>% 
  mutate(Outcome = 'naive') %>%
  rename(Actual=waterfall) %>%
  bind_cols(dataset_test %>% select(cell, experiment)) %>%
  mutate(Predicted=predict(fit1,dataset_test_temp))
```

Next use the posterior probability of sensitive.
```{r}
dataset_temp <- dataset %>% select(cell_type, ends_with('mutation'), ends_with('rna'), ends_with('cnv')) %>% mutate(cell_type=as.factor(cell_type))
fit1 <- randomForest(cell_type~.,data=dataset_temp,
                     ntree=pull(filter(best_params,outcome_variable=='cell_type'),ntree),
                     mtry=pull(filter(best_params,outcome_variable=='cell_type'),mtry))
posterior_imp <- importance(fit1) %>%
  as.data.frame() %>%
  rownames_to_column('feature') %>% 
  as_tibble() %>% 
  mutate(outcome_variable = 'posterior')

posterior_preds <- dataset_temp %>%
  select(cell_type) %>% 
  mutate(Outcome = 'posterior') %>%
  rename(Actual=cell_type) %>%
  bind_cols(dataset %>% select(cell, experiment)) %>%
  mutate(Predicted=fit1$predicted)

posterior_diagnostics <- confusionMatrix(posterior_preds$Actual, posterior_preds$Predicted)
```

Get test set (intermediate called by waterfall) predictions for this measure.
```{r}
dataset_test_temp <- dataset_test %>% select(cell_type, ends_with('mutation'), ends_with('rna'), ends_with('cnv')) %>% mutate(cell_type=as.factor(cell_type))
posterior_test_preds <- dataset_test %>%
  select(waterfall) %>% 
  mutate(Outcome = 'posterior') %>%
  rename(Actual=waterfall) %>%
  bind_cols(dataset_test %>% select(cell, experiment)) %>%
  mutate(Predicted=predict(fit1,dataset_test_temp))
```

Last for the waterfall.
```{r}
dataset_temp <- dataset %>% select(waterfall, ends_with('mutation'), ends_with('rna'), ends_with('cnv')) %>% 
  mutate(waterfall=as.character(waterfall)) %>%
  filter(waterfall != 'intermediate') %>%
  mutate(waterfall=as.factor(waterfall))
fit1 <- randomForest(waterfall~.,data=dataset_temp,
                     ntree=pull(filter(best_params,outcome_variable=='waterfall'),ntree),
                     mtry=pull(filter(best_params,outcome_variable=='waterfall'),mtry),)
waterfall_imp <- importance(fit1) %>%
  as.data.frame() %>%
  rownames_to_column('feature') %>% 
  as_tibble() %>% 
  mutate(outcome_variable = 'waterfall')

waterfall_preds <- dataset_temp %>%
  select(waterfall) %>% 
  mutate(Outcome = 'waterfall') %>%
  rename(Actual=waterfall) %>%
  bind_cols(dataset %>% filter(waterfall != 'intermediate') %>% select(cell, experiment)) %>%
  mutate(Predicted=fit1$predicted)


waterfall_diagnostics <- confusionMatrix(waterfall_preds$Actual, waterfall_preds$Predicted)
```

Get test set (intermediate called by waterfall) predictions for this measure.
```{r}
dataset_test_temp <- dataset_test %>% select(waterfall, ends_with('mutation'), ends_with('rna'), ends_with('cnv')) %>% mutate(waterfall=as.factor(waterfall))
waterfall_test_preds <- dataset_test %>%
  select(waterfall) %>% 
  mutate(Outcome = 'waterfall') %>%
  rename(Actual=waterfall) %>%
  bind_cols(dataset_test %>% select(cell, experiment)) %>%
  mutate(Predicted=predict(fit1,dataset_test_temp))
```

Join all importance and predictions together.
```{r}
all.importance <- bind_rows(waterfall_imp, posterior_imp, naive_imp)
all.predictions <- naive_preds %>% 
  bind_rows(posterior_preds, waterfall_preds) %>%
  left_join(dataset %>% select(cell, experiment, auc_recomputed, posterior_probability_sensitive), by=c('cell','experiment'))
all.diagnostics <- list(naive=naive_diagnostics, posterior=posterior_diagnostics, waterfall=waterfall_diagnostics)
```

Bind in test set.
```{r}
all.test.predictions <- naive_test_preds %>% 
  bind_rows(posterior_test_preds, waterfall_test_preds) %>%
  left_join(dataset_test %>% select(cell, experiment, auc_recomputed, posterior_probability_sensitive), by=c('cell','experiment'))
all.predictions <- all.predictions %>% bind_rows(all.test.predictions)
```

Load gene names.
```{r}
ensembl = biomaRt::useEnsembl(biomart="ensembl", dataset="hsapiens_gene_ensembl")
chr_genes <- biomaRt::getBM(attributes=c('ensembl_gene_id','ensembl_transcript_id','hgnc_symbol'), mart = ensembl) %>%
  as_tibble()
all.importance <- all.importance %>%
  separate(feature,into=c('feature','extra1','extra2'), fill='right',sep='_') %>% 
  left_join(chr_genes,by = c('feature'='ensembl_gene_id')) %>%
  mutate(symbol = ifelse(is.na(hgnc_symbol),feature, hgnc_symbol)) %>%
  mutate(type = ifelse(is.na(extra2),extra1, extra2))
```

Plot variable importance.
```{r}
p <- all.importance %>% 
  filter(MeanDecreaseGini>0) %>%
  mutate(wt = ifelse(outcome_variable=='posterior',1,0)) %>%
  mutate(outcome_variable = case_when(outcome_variable == 'posterior' ~ 'P(sensitive | AAC) > 0.5',
                                      outcome_variable == 'naive' ~ 'AAC > 0.2',
                                      outcome_variable == 'waterfall' ~ 'Waterfall method')) %>%
  mutate(type = case_when(type == 'mutation' ~ 'Mutation',
                          type == 'rna' ~ 'RNA-seq',
                          type == 'cnv' ~ 'CNV')) %>%
  ggplot(aes(x=reorder(symbol,MeanDecreaseGini*wt), y=MeanDecreaseGini, color=type, group=symbol)) +
  geom_point() +
  #geom_line(color='grey') +
  theme_bw() + 
  coord_flip() +
  facet_grid(cols=vars(outcome_variable)) + 
  labs(x='Feature',y='Mean Decrease Gini',color='Feature type') +
  scale_color_brewer(palette='Dark2') + 
  theme(legend.position='top')
ggsave(file.path(log_dir,'variable_importance.pdf'), p)
saveRDS(p,file.path(log_dir,'variable_importance.RDS'))
```

Print diagnostics.
```{r}
diagnostics <- lapply(1:length(all.diagnostics), function(jj) {
  print(names(all.diagnostics)[jj])
  print(all.diagnostics[[jj]]$table)
  data.frame(Value=all.diagnostics[[jj]]$byClass) %>% 
    rownames_to_column('Metric') %>%
    mutate(Outcome=names(all.diagnostics)[jj]) 
})
diagnostics <- do.call(bind_rows, diagnostics)
```

Plot diagnostics.
```{r}
p <- diagnostics %>% 
  ggplot(aes(x=Outcome, y=Value, fill=Outcome)) + 
  geom_bar(stat="identity") + 
  facet_wrap(vars(Metric), ncol=3) +
  theme_bw() + 
  scale_fill_brewer(palette='Dark2') + 
  theme(legend.position='top') + 
  labs(y='', x='', fill='', title='Best Model Fit Diagnostics by Outcome Measure')
ggsave(file.path(log_dir,'diagnostics.pdf'), p)
saveRDS(p,file.path(log_dir,'diagnostics.RDS'))
```

Plot predicted versus actual.
```{r}
dd1 <- all.predictions %>%
  select(Outcome, cell, experiment, Predicted, auc_recomputed, posterior_probability_sensitive) %>%
  rename(Call = Predicted) %>%
  mutate(Method = 'Predicted')
for (dat in datasets) {
  p <- all.predictions %>%
    filter(experiment==dat) %>%
    select(Outcome, cell, experiment, Actual, auc_recomputed, posterior_probability_sensitive) %>%
    rename(Call = Actual) %>%
    mutate(Method = 'Actual') %>%
    bind_rows(dd1 %>% filter(experiment==dat)) %>%
    na.omit() %>%
    mutate(hline = case_when(Outcome == 'posterior' ~ min_posterior_probability_sensitive,
                               Outcome == 'naive' ~ Inf,
                               Outcome == 'waterfall' ~ Inf)) %>%
    mutate(vline = case_when(Outcome == 'posterior' ~ Inf,
                               Outcome == 'naive' ~ .2,
                               Outcome == 'waterfall' ~ Inf)) %>%
    mutate(Outcome = case_when(Outcome == 'posterior' ~ 'P(sensitive | AAC) > 0.5',
                               Outcome == 'naive' ~ 'AAC > 0.2',
                               Outcome == 'waterfall' ~ 'Waterfall method')) %>%
    ggplot(aes(x=auc_recomputed,y=posterior_probability_sensitive, color=Call)) + 
    geom_point(alpha=.6) + 
    geom_hline(aes(yintercept=hline),lty=2) +
    geom_vline(aes(xintercept=vline),lty=2) +
    facet_grid(cols=vars(Outcome), rows=vars(Method)) +
    theme_bw() + 
    labs(y='Posterior probability sensitive',x='AAC', color='') + 
    theme(legend.position='top') + 
    scale_color_brewer(palette='Dark2')
  ggsave(file.path(log_dir,paste(dat,'predicted_v_actual.pdf',sep='_')), p)
  saveRDS(p,file.path(log_dir,paste(dat,'predicted_v_actual.RDS',sep='_')))
}
```
