---
title: "Introduction"
author: "Matt Ploenzke"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Estimate concordance}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Set up and load packages.
```{r setup, include=FALSE}
  rm(list=ls(all=TRUE))
  knitr::opts_chunk$set(echo = TRUE)
  library(PharmacoMixtuR)
  library(tidyverse)
  library(ggridges)
```

Set options.
```{r}
  opt <- list()
  opt$datasets <- c('CCLE','GDSC') # CCLE GDSC GDSC1000 gCSI FIMM CTRPv2
  opt$min_intersection <- 2 # Minimum number of studies a drug/cell must be assayed in to be included in the intersection comparison
  opt$log_dir <- paste(paste(opt$datasets,collapse='_'),'fit_p60',sep='_')
  opt$sensitivity_measure <- 'auc_recomputed' # raw_auc e_inf hill_slope ec50 auc_recomputed
  # Prior specifications denoting cell sensitivity and proportion of drugs broadly-active:
  opt$prior.sensitive <- .6 # .3 # prior specification denoting cell is sensitive if greater than this value
  opt$prior.broadly.active <- 'median_mad' #median .05 # prior specification denoting drug is broadly-active if probability cell is sensitive is greater than value
```

Set up log directory.
```{r}
  dir.create(opt$log_dir,showWarnings = FALSE)
  capture.output(opt, file = file.path(opt$log_dir,'model_Opts.csv'))
```

Load data.
```{r}
library(PharmacoGx)
data(CCLEsmall)
data(GDSCsmall)
CCLE <- CCLEsmall
GDSC <- GDSCsmall
rm(CCLEsmall, GDSCsmall)
```

Format the sensitivity data for each experiment. Find cells and drugs assayed across experiment. Remove noisy experiments and mislabelled cell lines. Calculate sensitivity measures per cell/drug.
```{r}
  sensitivity.tibble.list <- intersectPSetWrapper(datasets = opt$datasets,
                                                  minimum_intersection = 1,
                                                  intersectOn = NULL,
                                                  sensitivity_measure = opt$sensitivity_measure,
                                                  remove_noisy_curves = FALSE,
                                                  remove_mislabelled_cells = FALSE)
```

Repeat but for the intersection.
```{r}
  intersection.tibble.list <- intersectPSetWrapper(datasets = opt$datasets,
                                                  minimum_intersection = opt$min_intersection,
                                                  intersectOn = NULL,
                                                  sensitivity_measure = opt$sensitivity_measure,
                                                  remove_noisy_curves = FALSE,
                                                  remove_mislabelled_cells = FALSE)
  eval(parse(text=paste('rm(',paste(opt$datasets,collapse=','),')',sep='')))
  intersection.tibble.list <- lapply(intersection.tibble.list, function(ii) {
    ii %>% group_by(drug,cell,measure) %>% filter(n_distinct(experiment) >= opt$min_intersection) %>% ungroup()
  })
```

Initialize drug and cell assignments for EM using prior specifications for probability sensitive and probability drug is broadly active.
```{r}
drugs.tibble.list <- lapply(sensitivity.tibble.list, function(li) {
  drug_dat <- li %>% 
    mutate(all_median = quantile(value,opt$prior.sensitive),
           all_mad = stats::mad(value),
           drug=as.factor(drug)) %>% 
    group_by(drug) %>% 
    mutate(median=median(value),
           mad=stats::mad(value),
           all_median=first(all_median),
           all_mad=first(all_mad)) %>%
    ungroup() %>%
    mutate(drug_type = ifelse(median<=all_median & mad<=all_mad,'targeted','broad')) %>%
    distinct(drug, drug_type, all_median, all_mad, median, median, mad)
  li %>% 
    left_join(drug_dat, by='drug') %>%
    mutate(sensitive = ifelse(value > all_median, 1,0)) %>%
    group_by(drug, measure, drug_type) %>%
    summarise(p_prior = mean(sensitive),
              sensitive = sum(sensitive),
              cell_count = n()) %>%
    ungroup() %>% 
    select(drug, measure, p_prior, sensitive, cell_count, drug_type)
})
cells.tibble.list <- lapply(1:length(sensitivity.tibble.list), function(li) {
  sensitivity.tibble.list[[li]] %>% 
    left_join(drugs.tibble.list[[li]], by=c('drug','measure')) %>% 
    select(drug:measure,drug_type) %>%
    ungroup() %>% 
    group_by(experiment) %>%
    mutate(prior_threshold = quantile(value,probs = opt$prior.sensitive), 
           cell_type = ifelse(value>=prior_threshold,'sensitive','resistant')) %>%
    ungroup()
})
names(cells.tibble.list) <- names(drugs.tibble.list)
```

Using the assignments, fit distributions (first M step) and use these as priors to initialize EM with. 
```{r}
meas <- opt$sensitivity_measure[1]
drug_types_list <- lapply(drugs.tibble.list, function(tibb) {
  tibb %>%
    filter(measure==meas) %>%
    group_by(drug_type) %>%
    do(mutate(fit_bb_mle(.$sensitive, .$cell_count), number = nrow(.))) %>%
    ungroup() %>%
    mutate(drug_type_prior = number / sum(number))
})
targetted_drug_fits_list <- lapply(cells.tibble.list, function(tibb) {
  ttibb <- tibb %>%
    filter(measure==meas) %>%
    mutate(value = ifelse(value<1e-3,1e-3,value)) %>%
    mutate(drug_type = 'targeted') %>%
    group_by(drug, cell_type, drug_type, experiment) %>%
    do(mutate(fit_beta_mle(.$value),number = nrow(.))) %>%
    group_by(drug, drug_type, experiment) %>%
    mutate(ndist=n_distinct(cell_type)) %>%
    ungroup()
  ttibb %>%
    bind_rows(
      ttibb %>% 
        filter(ndist<2) %>% 
        mutate(cell_type2 = case_when(cell_type=='resistant' ~ 'sensitive',cell_type=='sensitive' ~ 'resistant'),
               cell_type=cell_type2,
               number=0,
               alpha=case_when(cell_type == 'resistant' ~ 1.5,
                               cell_type == 'sensitive' ~ 50),
               beta=case_when(cell_type == 'resistant' ~ 7.5,
                              cell_type == 'sensitive' ~ 50)) %>%
        select(-cell_type2)
    ) %>%
    group_by(drug, experiment) %>%       
    mutate(targeted_cell_type_prior = number / sum(number)) %>%
    mutate(targeted_cell_type_prior = pmax(pmin(targeted_cell_type_prior, .99),.01)) %>%
    ungroup() %>% 
    select(-ndist)
})
broad_drug_fits_list <- lapply(cells.tibble.list, function(tibb) {
  tibb %>%
    filter(measure==meas) %>%
    mutate(x=ifelse(value<1e-3,1e-3,value)) %>%
    group_by(drug, experiment) %>%
    do(mutate(fit_beta_mle(.$x),
              number = nrow(.),
              broad_cell_type_prior = mean(.$value>=.$prior_threshold))) %>%
    ungroup() %>% 
    mutate(drug_type = 'broad') %>%
    select(drug, drug_type, alpha, beta, number, broad_cell_type_prior, experiment)
})
targeted_drug_priors <- lapply(1:length(targetted_drug_fits_list), function(num) {
  targetted_drug_fits_list[[num]] %>% 
    rename(cell_type_prior = targeted_cell_type_prior) %>%
    select(drug, drug_type, cell_type_prior, experiment, cell_type) %>%
    mutate(drug_type = 'broad')
})
broad_drug_priors <- lapply(1:length(broad_drug_fits_list), function(num) {
  broad_drug_fits_list[[num]] %>%
    rename(cell_type_prior = broad_cell_type_prior) %>%
    select(drug, drug_type, cell_type_prior, experiment) %>%
    mutate(drug_type = 'targeted')
})
```

Perform an expectation step using the distributions to initialize for the EM. 
```{r}
targetted_cell_assignments_list <- lapply(1:length(targetted_drug_fits_list), function(num) {
  targetted_drug_list <- unique(targetted_drug_fits_list[[num]]$drug)
  targetted_cell_assignments <- lapply(targetted_drug_list, function(dr) {
    cells.tibble.list[[num]] %>%
      filter(drug == dr,measure==meas) %>%
      select(drug:measure) %>%
      mutate(drug_type = 'targeted') %>%
      mutate(value=ifelse(value<1e-3,1e-3,value)) %>%
      crossing(targetted_drug_fits_list[[num]] %>% filter(drug == dr) %>% select(-drug,-drug_type) %>% rename(experiment1=experiment)) %>%
      filter(experiment==experiment1) %>% 
      select(-experiment1) %>% 
      mutate(median = qbeta(.5,alpha,beta),
             likelihood = dbeta(value, alpha, beta)) %>% 
      group_by(cell_type) %>%
      mutate(max.likelihood=max(likelihood)) %>%
      ungroup() %>%
      mutate(likelihood = case_when(value>median & cell_type == 'sensitive' ~ max.likelihood-likelihood + max.likelihood, 
                                    value<median & cell_type == 'resistant' ~ max.likelihood-likelihood + max.likelihood, 
                                    TRUE~likelihood)) %>%
      mutate(likelihood = targeted_cell_type_prior * likelihood) %>%
      group_by(drug, cell, experiment) %>%
      mutate(posterior=exp(log(likelihood)-log(sum(likelihood)))) %>% 
      top_n(1, likelihood) %>%
      ungroup()
  })
  do.call(bind_rows, targetted_cell_assignments)
})
broad_cell_assignments_list <- lapply(1:length(broad_drug_fits_list), function(num) {
  cells.tibble.list[[num]] %>%
      filter(drug %in% unique(broad_drug_fits_list[[num]]$drug),measure==meas) %>%
      select(drug:measure) %>%
      mutate(drug_type = 'broad') %>%
      mutate(value=ifelse(value<1e-3,1e-3,value)) %>%
      left_join(broad_drug_fits_list[[num]], by=c('drug','drug_type', 'experiment')) %>%
      mutate(likelihood = dbeta(value, alpha, beta),
             cell_type = ifelse((broad_cell_type_prior*pbeta(value, alpha, beta)) >
                                  ((1-broad_cell_type_prior)*(1-pbeta(value, alpha, beta))),
                                'sensitive','resistant'))
})

drugs.tibble.list <- lapply(1:length(drugs.tibble.list), function(num) {
  targetteds <- drugs.tibble.list[[num]] %>%
    filter(measure==meas) %>%
    select(drug, measure) %>%
    right_join(targetted_cell_assignments_list[[num]] %>% select(drug, cell, cell_type, likelihood), by='drug') %>% 
    group_by(drug, measure) %>%
    summarise(sensitive = sum(cell_type=='sensitive'),
              cell_count = n()) %>%
    ungroup() %>% 
    mutate(type='targeted')
  broads <- drugs.tibble.list[[num]] %>%
    filter(measure==meas) %>%
    select(drug, measure) %>%
    right_join(broad_cell_assignments_list[[num]] %>% select(drug, cell, cell_type), by='drug') %>% 
    group_by(drug, measure) %>%
    summarise(sensitive = sum(cell_type=='sensitive'),
              cell_count = n()) %>%
    ungroup() %>%
    mutate(type='broad')
  bind_rows(targetteds, broads)
})

drug_assignments_list <- lapply(1:length(drugs.tibble.list), function(num) {
  drugs.tibble.list[[num]] %>%
    filter(measure==meas) %>%
    rename(drug_type = type) %>%
    right_join(drug_types_list[[num]] %>% select(-number), by='drug_type') %>%
    mutate(likelihood = drug_type_prior * VGAM::dbetabinom.ab(sensitive, cell_count, alpha, beta)) %>%
    group_by(drug) %>%
    mutate(posterior=likelihood/sum(likelihood)) %>% 
    top_n(1, likelihood) %>%
    ungroup()
})

cell_assignments_list <- lapply(1:length(targetted_cell_assignments_list), function(num) {
  bind_rows(targetted_cell_assignments_list[[num]],broad_cell_assignments_list[[num]]) %>%
    left_join(targeted_drug_priors[[num]], by=c('drug','experiment','drug_type','cell_type')) %>%
    mutate(targeted_cell_type_prior = case_when(is.na(targeted_cell_type_prior) & drug_type=='broad' ~ cell_type_prior,
                                                TRUE ~ targeted_cell_type_prior)) %>%
    select(-cell_type_prior) %>%
    left_join(broad_drug_priors[[num]],  by=c('drug','experiment','drug_type')) %>%
    mutate(broad_cell_type_prior = case_when(is.na(broad_cell_type_prior) & drug_type=='targeted' ~ cell_type_prior,
                                                TRUE ~ broad_cell_type_prior)) %>%
    select(-cell_type_prior) %>%
    right_join(drug_assignments_list[[num]] %>% select(drug, drug_type), by=c('drug','drug_type')) %>% 
    select(drug, cell, value, experiment, measure, drug_type, cell_type, broad_cell_type_prior, targeted_cell_type_prior)
})
names(cell_assignments_list) <- names(drug_types_list)
```

Run EM.
```{r}
  iterations_list <- list()
  for(num in 1:length(cell_assignments_list)) {
    drug_assignments <- drug_assignments_list[[num]]
    cell_assignments <- cell_assignments_list[[num]]
    targeted_priors <- targeted_drug_priors[[num]]
    broad_priors <- broad_drug_priors[[num]]
    iterations_list[[num]] <- accumulate(1:5, iterate_em, .init = list(drug_assignments = drug_assignments,
                                                                       cell_assignments = cell_assignments,
                                                                       targeted_priors = targeted_priors,
                                                                       broad_priors = broad_priors))
  }
  names(iterations_list) <- names(sensitivity.tibble.list)
```

Obtain posterior information from last EM rep.
```{r}
  posterior_drug_types_list <- lapply(names(iterations_list), function(num) {
    iterations_list[[num]] %>% 
      map_df("drug_types", .id = "iteration") %>% 
      mutate(iteration = as.numeric(iteration)) %>%
      filter(iteration==max(iteration))
  })
  posterior_drug_assignments_list <- lapply(names(iterations_list), function(num) {
    iterations_list[[num]] %>% 
      map_df("drug_assignments", .id = "iteration") %>% 
      mutate(iteration = as.numeric(iteration)) %>%
      filter(iteration==max(iteration))
  })
  posterior_drug_fits_list <- lapply(names(iterations_list), function(num) {
    iterations_list[[num]] %>% 
      map_df("drug_fits", .id = "iteration") %>% 
      mutate(iteration = as.numeric(iteration)) %>%
      filter(iteration==max(iteration))
  })
  posterior_cell_assignments_list <- lapply(names(iterations_list), function(num) {
    iterations_list[[num]] %>% 
      map_df("cell_assignments", .id = "iteration") %>% 
      mutate(iteration = as.numeric(iteration)) %>%
      filter(iteration==max(iteration))
  })
  names(posterior_cell_assignments_list) <- names(iterations_list)
```

Do one more rep.
```{r}
  posteriors_list <- list()
  for(num in 1:length(cell_assignments_list)) {
    drug_assignments <- posterior_drug_assignments_list[[num]] %>% select(-iteration)
    cell_assignments <- posterior_cell_assignments_list[[num]]  %>% select(-iteration)
    targeted_priors <- targeted_drug_priors[[num]]
    broad_priors <- broad_drug_priors[[num]]
    posteriors_list[[num]] <- accumulate(1, iterate_em, .init = list(drug_assignments = drug_assignments,
                                                                 cell_assignments = cell_assignments,
                                                                  targeted_priors = targeted_priors,
                                                                       broad_priors = broad_priors),
                                         last=TRUE)
  }
  names(posteriors_list) <- names(sensitivity.tibble.list)
  
  posterior_drug_types_full <- lapply(names(posteriors_list), function(num) {
    posteriors_list[[num]] %>% 
      map_df("drug_types", .id = "iteration") %>% 
      mutate(iteration = as.numeric(iteration)) %>%
      filter(iteration==max(iteration))
  })
  posterior_drug_assignments_full <- lapply(names(posteriors_list), function(num) {
    posteriors_list[[num]] %>% 
      map_df("drug_assignments", .id = "iteration") %>%
      mutate(iteration = as.numeric(iteration)) %>%
      filter(iteration==max(iteration))
  })
  posterior_drug_fits_full <- lapply(names(posteriors_list), function(num) {
    posteriors_list[[num]] %>% 
      map_df("drug_fits", .id = "iteration") %>% 
      mutate(iteration = as.numeric(iteration)) %>%
      filter(iteration==max(iteration))
  })
  posterior_cell_assignments_full <- lapply(names(posteriors_list), function(num) {
    posteriors_list[[num]] %>% 
      map_df("cell_assignments", .id = "iteration") %>% 
      mutate(iteration = as.numeric(iteration)) %>%
      filter(iteration==max(iteration))
  })
  names(posterior_cell_assignments_full) <- names(posteriors_list)
```

Format posterior agreements.
```{r}
  posterior_drug_types <- do.call(bind_rows,posterior_drug_types_list) %>%
    mutate(experiment=rep(names(iterations_list),each=2)) 
  nums <- sapply(posterior_drug_assignments_list, nrow)
  posterior_drug_assignments <- do.call(bind_rows,posterior_drug_assignments_list) %>%
      mutate(experiment=rep(names(iterations_list),times=nums))
  nums <- sapply(posterior_drug_fits_list, nrow)
  posterior_drug_fits <-  do.call(bind_rows,posterior_drug_fits_list) %>%
      mutate(experiment=rep(names(iterations_list),times=nums))
  nums <- sapply(posterior_cell_assignments_list, nrow)
  posterior_cell_assignments <- do.call(bind_rows,posterior_cell_assignments_list) %>%
      mutate(experiment=rep(names(iterations_list),times=nums))
  
  posterior_drug_types <- do.call(bind_rows,posterior_drug_types_full) %>%
    mutate(experiment=rep(names(posteriors_list),each=2)) 
  nums <- sapply(posterior_drug_assignments_full, nrow)
  posterior_drug_assignments <- do.call(bind_rows,posterior_drug_assignments_full) %>%
      mutate(experiment=rep(names(posteriors_list),times=nums))
  nums <- sapply(posterior_drug_fits_full, nrow)
  posterior_drug_fits <-  do.call(bind_rows,posterior_drug_fits_full) %>%
      mutate(experiment=rep(names(posteriors_list),times=nums))
  nums <- sapply(posterior_cell_assignments_full, nrow)
  posterior_cell_assignments <- do.call(bind_rows,posterior_cell_assignments_full) %>%
      mutate(experiment=rep(names(posteriors_list),times=nums))
```

Format a big data frame with all relevant posterior information.
```{r}
posterior <- posterior_cell_assignments %>%
  select(drug, cell, experiment, drug_type, cell_type, posterior, likelihood, value) %>%
  rename(cell_type_posterior=posterior,
         cell_type_likelihood=likelihood,
         realized_value=value) %>%
  group_by(drug, cell) %>% 
  mutate(num_experiments = n_distinct(experiment)) %>%
  ungroup() %>%
  left_join(posterior_drug_assignments %>%
              select(drug, drug_type, posterior,likelihood, experiment) %>%
              rename(drug_type_posterior=posterior,
                     drug_type_likelihood=likelihood), by=c('drug_type','drug','experiment')) %>%
  mutate(cell_type = ifelse(cell_type == 'sensitive' & drug_type == 'broad',
                            'resistant',cell_type)) %>%
  left_join(posterior_drug_fits %>%
              select(drug, cell_type, experiment, alpha, beta, drug_type),
            by = c('drug','cell_type','experiment','drug_type')) %>%
  mutate(cell_type_posterior = case_when(drug_type == 'broad' ~ pbeta(realized_value, alpha, beta, lower.tail = FALSE),
                                         TRUE ~ cell_type_posterior)) %>%
  select(-alpha, -beta) %>%
  mutate(cell_type_posterior = ifelse((cell_type == 'resistant' & drug_type == 'targeted') | drug_type=='broad',
                                      1-cell_type_posterior,cell_type_posterior)) %>%
  mutate(drug_type_posterior = ifelse(drug_type == 'broad', 1-drug_type_posterior,drug_type_posterior)) %>%
  rename(posterior_probability_sensitive = cell_type_posterior,
         posterior_probability_targeted = drug_type_posterior)
saveRDS(object=posterior,file=file.path(opt$log_dir,'posterior.formatted.RDS'))
```
